### 2014-10-15 paper/paper.tex
latex template ACM 'tight' added

\documentclass{sig-alternate}

\begin{document}
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}

\title{State of the art in {\ttlit Sentiment Analysis}}

%\subtitle{}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
C. B. Hotz-Behofsits\\
       \affaddr{0929002}\\
       \affaddr{christian.hotz-behofsits@tuwien.ac.at}
% 2nd. author
\alignauthor
Thomas Schmidtleitner\\
       \affaddr{1025525}\\
       \affaddr{e1025525@student.tuwien.ac.at}
% 3rd. author
\alignauthor
Dominik Pichler\\
       \affaddr{1026045}\\
       \affaddr{dominik.pichler@aon.at}
\and  % use '\and' if you need 'another row' of author names
% 4th. author
\alignauthor
Matthias Reisinger\\
       \affaddr{1025631}\\
       \affaddr{matthias.reisinger@web0.at}
% 5th. author
\alignauthor
Florian Taus\\
       \affaddr{0627918}\\
       \affaddr{florian.taus@hotmail.com}
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a sample of a \LaTeX\ document which conforms,
somewhat loosely, to the formatting guidelines for
ACM SIG Proceedings. It is an {\em alternate} style which produces
a {\em tighter-looking} paper and was designed in response to
concerns expressed, by authors, over page-budgets.
It complements the document \textit{Author's (Alternate) Guide to
Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
This source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file. A compiled PDF version
is available on the web page to help you with the
`look and feel'.
\end{abstract}

% A category with the (minimum) three required fields
\category{H.4}{Information Systems Applications}{Miscellaneous}
%A category including the fourth, optional field follows...
\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]

\terms{Theory}

\keywords{ACM proceedings, \LaTeX, text tagging}

\section{Introduction}
The \textit{proceedings} are the records of a conference.
ACM seeks to give these conference by-products a uniform,
high-quality appearance.  To do this, ACM has some rigid
requirements for the format of the proceedings documents: there
is a specified format (balanced  double columns), a specified
set of fonts (Arial or Helvetica and Times Roman) in
certain specified sizes (for instance, 9 point for body copy),
a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
and (1.9 cm [.75"]) left and right; specified column width
(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

The good news is, with only a handful of manual
settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
and {\texttt{\char'134 alignauthor}} commands, you have
already used; another, {\texttt{\char'134 balancecolumns}}, will
be used in your very last run of \LaTeX\ to ensure
balanced column heights on the last page.}, the \LaTeX\ document
class file handles all of this for you.

The remainder of this document is concerned with showing, in
the context of an ``actual'' document, the \LaTeX\ commands
specifically available for denoting the structure of a
proceedings paper, rather than with giving rigorous descriptions
or explanations of such commands.

\section{The {\secit Body} of The Paper}
Typically, the body of a paper is organized
into a hierarchical structure, with numbered or unnumbered
headings for sections, subsections, sub-subsections, and even
smaller sections.  The command \texttt{{\char'134}section} that
precedes this paragraph is part of such a
hierarchy.\footnote{This is the second footnote.  It
starts a series of three footnotes that add nothing
informational, but just give an idea of how footnotes work
and look. It is a wordy one, just so you see
how a longish one plays out.} \LaTeX\ handles the numbering
and placement of these headings for you, when you use
the appropriate heading commands around the titles
of the headings.  If you want a sub-subsection or
smaller part to be unnumbered in your output, simply append an
asterisk to the command name.  Examples of both
numbered and unnumbered headings will appear throughout the
balance of this sample document.

Because the entire article is contained in
the \textbf{document} environment, you can indicate the
start of a new paragraph with a blank line in your
input file; that is why this sentence forms a separate paragraph.

\subsection{Type Changes and {\subsecit Special} Characters}
We have already seen several typeface changes in this sample.  You
can indicate italicized words or phrases in your text with
the command \texttt{{\char'134}textit}; emboldening with the
command \texttt{{\char'134}textbf}
and typewriter-style (for instance, for computer code) with
\texttt{{\char'134}texttt}.  But remember, you do not
have to indicate typestyle changes when such changes are
part of the \textit{structural} elements of your
article; for instance, the heading of this subsection will
be in a sans serif\footnote{A third footnote, here.
Let's make this a rather short one to
see how it looks.} typeface, but that is handled by the
document class file. Take care with the use
of\footnote{A fourth, and last, footnote.}
the curly braces in typeface changes; they mark
the beginning and end of
the text that is to be in the different typeface.

You can use whatever symbols, accented characters, or
non-English characters you need anywhere in your document;
you can find a complete list of what is
available in the \textit{\LaTeX\
User's Guide}\cite{Lamport:LaTeX}.

\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\subsubsection{Inline (In-text) Equations}
A formula that appears in the running text is called an
inline or in-text formula.  It is produced by the
\textbf{math} environment, which can be
invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
construction or with the short form \texttt{\$. . .\$}. You
can use any of the symbols and structures,
from $\alpha$ to $\omega$, available in
\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
few examples of in-text equations in context. Notice how
this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
set here in in-line math style, looks slightly different when
set in display style.  (See next section).

\subsubsection{Display Equations}
A numbered display equation -- one set off by vertical space
from the text and centered horizontally -- is produced
by the \textbf{equation} environment. An unnumbered display
equation is produced by the \textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols
and structures available in \LaTeX; this section will just
give a couple of examples of display equations in context.
First, consider the equation, shown as an inline equation above:
\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
Notice how it is formatted somewhat differently in
the \textbf{displaymath}
environment.  Now, we'll enter an unnumbered equation:
\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
and follow it with another numbered equation:
\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
just to demonstrate \LaTeX's able handling of numbering.

\subsection{Citations}
Citations to articles \cite{bowman:reasoning,
clark:pct, braams:babel, herlihy:methodology},
conference proceedings \cite{clark:pct} or
books \cite{salas:calculus, Lamport:LaTeX} listed
in the Bibliography section of your
article will occur throughout the text of your article.
You should use BibTeX to automatically produce this bibliography;
you simply need to insert one of several citation commands with
a key of the item cited in the proper location in
the \texttt{.tex} file \cite{Lamport:LaTeX}.
The key is a short reference you invent to uniquely
identify each work; in this sample document, the key is
the first author's surname and a
word from the title.  This identifying key is included
with each item in the \texttt{.bib} file for your article.

The details of the construction of the \texttt{.bib} file
are beyond the scope of this sample document, but more
information can be found in the \textit{Author's Guide},
and exhaustive details in the \textit{\LaTeX\ User's
Guide}\cite{Lamport:LaTeX}.

This article shows only the plainest form
of the citation command, using \texttt{{\char'134}cite}.
This is what is stipulated in the SIGS style specifications.
No other citation format is endorsed or supported.

\subsection{Tables}
Because tables cannot be split across pages, the best
placement for them is typically the top of the page
nearest their initial cite.  To
ensure this proper ``floating'' placement of tables, use the
environment \textbf{table} to enclose the table's contents and
the table caption.  The contents of the table itself must go
in the \textbf{tabular} environment, to
be aligned properly in rows and columns, with the desired
horizontal and vertical rules.  Again, detailed instructions
on \textbf{tabular} material
is found in the \textit{\LaTeX\ User's Guide}.

Immediately following this sentence is the point at which
Table 1 is included in the input file; compare the
placement of the table here with the table in the printed
dvi output of this document.

\begin{table}
\centering
\caption{Frequency of Special Characters}
\begin{tabular}{|c|c|l|} \hline
Non-English or Math&Frequency&Comments\\ \hline
\O & 1 in 1,000& For Swedish names\\ \hline
$\pi$ & 1 in 5& Common in math\\ \hline
\$ & 4 in 5 & Used in business\\ \hline
$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
\hline\end{tabular}
\end{table}

To set a wider table, which takes up the whole width of
the page's live area, use the environment
\textbf{table*} to enclose the table's contents and
the table caption.  As with a single-column table, this wide
table will ``float" to a location deemed more desirable.
Immediately following this sentence is the point at which
Table 2 is included in the input file; again, it is
instructive to compare the placement of the
table here with the table in the printed dvi
output of this document.

\begin{table*}
\centering
\caption{Some Typical Commands}
\begin{tabular}{|c|c|l|} \hline
Command&A Number&Comments\\ \hline
\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
\texttt{{\char'134}table}& 300 & For tables\\ \hline
\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\subsection{Figures}
Like tables, figures cannot be split across pages; the
best placement for them
is typically the top or the bottom of the page nearest
their initial cite.  To ensure this proper ``floating'' placement
of figures, use the environment
\textbf{figure} to enclose the figure and its caption.

This sample document contains examples of \textbf{.eps}
and \textbf{.ps} files to be displayable with \LaTeX.  More
details on each of these is found in the \textit{Author's Guide}.

%\begin{figure}
%centering
%\epsfig{file=fly.eps}
%\caption{A sample black and white graphic (.eps format).}
%\end{figure}

%\begin{figure}
%\centering
%\epsfig{file=fly.eps, height=1in, width=1in}
%\caption{A sample black and white graphic (.eps format)
%that has been resized with the \texttt{epsfig} command.}
%\end{figure}

As was the case with tables, you may want a figure
that spans two columns.  To do this, and still to
ensure proper ``floating'' placement of tables, use the environment
\textbf{figure*} to enclose the figure and its caption.
and don't forget to end the environment with
{figure*}, not {figure}!

Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
used; use
the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
commands as appropriate for the different file types.

\subsection{Theorem-like Constructs}
Other common constructs that may occur in your article are
the forms for logical constructs like theorems, axioms,
corollaries and proofs.  There are
two forms, one produced by the
command \texttt{{\char'134}newtheorem} and the
other by the command \texttt{{\char'134}newdef}; perhaps
the clearest and easiest way to distinguish them is
to compare the two in the output of this sample document:

This uses the \textbf{theorem} environment, created by
the\linebreak\texttt{{\char'134}newtheorem} command:
\newtheorem{theorem}{Theorem}
\begin{theorem}
Let $f$ be continuous on $[a,b]$.  If $G$ is
an antiderivative for $f$ on $[a,b]$, then
\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
\end{theorem}

The other uses the \textbf{definition} environment, created
by the \texttt{{\char'134}newdef} command:
\newdef{definition}{Definition}
\begin{definition}
If $z$ is irrational, then by $e^z$ we mean the
unique number which has
logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
\end{definition}

Two lists of constructs that use one of these
forms is given in the
\textit{Author's  Guidelines}.

There is one other similar construct environment, which is
already set up
for you; i.e. you must \textit{not} use
a \texttt{{\char'134}newdef} command to
create it: the \textbf{proof} environment.  Here
is a example of its use:
\begin{proof}
Suppose on the contrary there exists a real number $L$ such that
\begin{displaymath}
\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
\end{displaymath}
Then
\begin{displaymath}
l=\lim_{x\rightarrow c} f(x)
= \lim_{x\rightarrow c}
\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
\frac{f(x)}{g(x)} = 0\cdot L = 0,
\end{displaymath}
which contradicts our assumption that $l\neq 0$.
\end{proof}

Complete rules about using these environments and using the
two different creation commands are in the
\textit{Author's Guide}; please consult it for more
detailed instructions.  If you need to use another construct,
not listed therein, which you want to have the same
formatting as the Theorem
or the Definition\cite{salas:calculus} shown above,
use the \texttt{{\char'134}newtheorem} or the
\texttt{{\char'134}newdef} command,
respectively, to create it.

\subsection*{A {\secit Caveat} for the \TeX\ Expert}
Because you have just been given permission to
use the \texttt{{\char'134}newdef} command to create a
new form, you might think you can
use \TeX's \texttt{{\char'134}def} to create a
new command: \textit{Please refrain from doing this!}
Remember that your \LaTeX\ source code is primarily intended
to create camera-ready copy, but may be converted
to other forms -- e.g. HTML. If you inadvertently omit
some or all of the \texttt{{\char'134}def}s recompilation will
be, to say the least, problematic.

\section{Conclusions}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.
%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This section is optional; it is a location for you
to acknowledge grants, funding, editing assistance and
what have you.  In the present case, for example, the
authors would like to thank Gerald Murray of ACM for
his help in codifying this \textit{Author's Guide}
and the \textbf{.cls} and \textbf{.tex} files that it describes.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\appendix
%Appendix A
\section{Headings in Appendices}
The rules about hierarchical headings discussed above for
the body of the article are different in the appendices.
In the \textbf{appendix} environment, the command
\textbf{section} is used to
indicate the start of each Appendix, with alphabetic order
designation (i.e. the first is A, the second B, etc.) and
a title (if you include one).  So, if you need
hierarchical structure
\textit{within} an Appendix, start with \textbf{subsection} as the
highest level. Here is an outline of the body of this
document in Appendix-appropriate form:
\subsection{Introduction}
\subsection{The Body of the Paper}
\subsubsection{Type Changes and  Special Characters}
\subsubsection{Math Equations}
\paragraph{Inline (In-text) Equations}
\paragraph{Display Equations}
\subsubsection{Citations}
\subsubsection{Tables}
\subsubsection{Figures}
\subsubsection{Theorem-like Constructs}
\subsubsection*{A Caveat for the \TeX\ Expert}
\subsection{Conclusions}
\subsection{Acknowledgments}
\subsection{Additional Authors}
This section is inserted by \LaTeX; you do not insert it.
You just add the names and information in the
\texttt{{\char'134}additionalauthors} command at the start
of the document.
\subsection{References}
Generated by bibtex from your ~.bib file.  Run latex,
then bibtex, then latex twice (to resolve references)
to create the ~.bbl file.  Insert that ~.bbl file into
the .tex source file and comment out
the command \texttt{{\char'134}thebibliography}.
% This next section command marks the start of
% Appendix B, and does not continue the present hierarchy
\section{More Help for the Hardy}
The sig-alternate.cls file itself is chock-full of succinct
and helpful comments.  If you consider yourself a moderately
experienced to expert user of \LaTeX, you may find reading
it useful but please remember not to change it.
%\balancecolumns % GM June 2007
% That's all folks!
\end{document}

### 2014-10-16 src/com/aic/preprocessing/Process.java
processing boilerplate

@@ -1,0 +1,54 @@
+package com.aic.preprocessor
+
+public class Process {
+
+
+	/**
+	 * do all preprocessing steps at once
+	 *
+	 * @param String input content of a tweet
+	 */
+	public static String do(String input){
+
+	}
+
+	/**
+	 * filter unuseful words
+	 */
+	public static List<Token> filter(List<Token> tokens){
+		return removeArtiles(input);
+	}
+
+	/**
+	 * transform word
+	 * example: verb to noun
+	 *
+	 * @param String input multiple words
+	 */
+	public static Token transform(Token input){
+
+	}
+
+
+
+
+
+
+
+	/**
+	 *
+	 */
+	private static Token verbToNoun(Token verb){
+
+	}
+
+
+
+
+
+	/**
+	 * remove articles
+	 */
+	private static List<Token> removeArtiles(List<Token> tokens){}
+
+}

### 2014-10-16 src/com/aic/preprocessing/Token.java

@@ -1,0 +1,35 @@
+package com.aic.preprocessor
+
+public class Token{
+	TokenType type;
+	String token;
+	String value;
+
+	Token(String word){
+		if(word == null)
+			throw new WrongTokenFormatException('words should not be null');
+
+		if(word.length() < 1)
+			throw new WrongTokenFormatException('words should have at least one character');
+
+		if(word.contains(" "))
+			throw new WrongTokenFormatException('words should not contain space');
+
+		//TODO: Satzzeichen
+		switch(word.charAt(0)){
+			case '#':
+				type = TokenType.TAG;
+				value = word.substring(1);
+				break;
+			case '@':
+				type = TokenType.MENTIONING;
+				value = word.substring(1);
+				break;
+			default:
+				type = TokenType.WORD;
+				value = word;
+		}
+
+		token = word;
+	}
+}

### 2014-10-16 src/com/aic/preprocessing/TokenType.java

@@ -1,0 +1,5 @@
+package com.aic.preprocessor
+
+public enum TokenType {
+   TAG, MENTIONING, WORD, PUNCTATION
+}

### 2014-10-16 src/com/aic/preprocessing/WrongTokenFormatException.java

@@ -1,0 +1,9 @@
+
+public class WrongTokenFormatException extends Exception{
+      public WrongTokenFormatException() {}
+
+      //Constructor that accepts a message
+      public WrongTokenFormatException(String message){
+         super(message);
+      }
+ }

### 2014-10-16 src/com/aic/preprocessing/Process.java
bugfixes

@@ -1,22 +1,26 @@
-package com.aic.preprocessor
+package com.aic.preprocessor;
+
+import java.util.List;
 
 public class Process {
 
+
+	private String input = new String();
 
 	/**
 	 * do all preprocessing steps at once
 	 *
 	 * @param String input content of a tweet
 	 */
-	public static String do(String input){
-
+	public static String preprocess(String input){
+		return null;
 	}
 
 	/**
 	 * filter unuseful words
 	 */
 	public static List<Token> filter(List<Token> tokens){
-		return removeArtiles(input);
+		return removeArtiles(tokens);
 	}
 
 	/**
@@ -26,7 +30,7 @@ public class Process {
 	 * @param String input multiple words
 	 */
 	public static Token transform(Token input){
-
+		return null;
 	}
 
 
@@ -39,7 +43,7 @@ public class Process {
 	 *
 	 */
 	private static Token verbToNoun(Token verb){
-
+		return null;
 	}
 
 
@@ -49,6 +53,8 @@ public class Process {
 	/**
 	 * remove articles
 	 */
-	private static List<Token> removeArtiles(List<Token> tokens){}
+	private static List<Token> removeArtiles(List<Token> tokens){
+		return null;
+	}
 
 }

### 2014-10-16 src/com/aic/preprocessing/Test.java

@@ -1,0 +1,10 @@
+package com.aic.preprocessor;
+
+/*
+	Testklasse
+*/
+public class Test {
+	public static void main(String[] args){
+		System.out.println("Hello World!");
+	}
+}

### 2014-10-16 src/com/aic/preprocessing/Token.java

@@ -1,19 +1,19 @@
-package com.aic.preprocessor
+package com.aic.preprocessor;
 
 public class Token{
 	TokenType type;
 	String token;
 	String value;
 
-	Token(String word){
+	Token(String word) throws WrongTokenFormatException{
 		if(word == null)
-			throw new WrongTokenFormatException('words should not be null');
+			throw new WrongTokenFormatException("words should not be null");
 
 		if(word.length() < 1)
-			throw new WrongTokenFormatException('words should have at least one character');
+			throw new WrongTokenFormatException("words should have at least one character");
 
 		if(word.contains(" "))
-			throw new WrongTokenFormatException('words should not contain space');
+			throw new WrongTokenFormatException("words should not contain space");
 
 		//TODO: Satzzeichen
 		switch(word.charAt(0)){

### 2014-10-16 src/com/aic/preprocessing/TokenType.java

@@ -1,4 +1,4 @@
-package com.aic.preprocessor
+package com.aic.preprocessor;
 
 public enum TokenType {
    TAG, MENTIONING, WORD, PUNCTATION

### 2014-10-16 src/com/aic/preprocessing/WrongTokenFormatException.java

@@ -1,3 +1,4 @@
+package com.aic.preprocessor;
 
 public class WrongTokenFormatException extends Exception{
       public WrongTokenFormatException() {}

### 2014-10-16 src/main/java/com/aic/preprocessing/Process.java
refactored

@@ -1,4 +1,4 @@
-package com.aic.preprocessor;
+package com.aic.preprocessing;
 
 import java.util.List;
 

### 2014-10-16 src/main/java/com/aic/preprocessing/Test.java

@@ -1,4 +1,4 @@
-package com.aic.preprocessor;
+package com.aic.preprocessing;
 
 /*
 	Testklasse

### 2014-10-16 src/main/java/com/aic/preprocessing/Token.java

@@ -1,4 +1,4 @@
-package com.aic.preprocessor;
+package com.aic.preprocessing;
 
 public class Token{
 	TokenType type;

### 2014-10-16 src/main/java/com/aic/preprocessing/TokenType.java

@@ -1,4 +1,4 @@
-package com.aic.preprocessor;
+package com.aic.preprocessing;
 
 public enum TokenType {
    TAG, MENTIONING, WORD, PUNCTATION

### 2014-10-16 src/main/java/com/aic/preprocessing/WrongTokenFormatException.java

@@ -1,4 +1,4 @@
-package com.aic.preprocessor;
+package com.aic.preprocessing;
 
 public class WrongTokenFormatException extends Exception{
       public WrongTokenFormatException() {}

### 2014-10-16 src/main/java/com/aic/preprocessing/Token.java
refactored test added

@@ -5,7 +5,7 @@ public class Token{
 	String token;
 	String value;
 
-	Token(String word) throws WrongTokenFormatException{
+	public Token(String word) throws WrongTokenFormatException{
 		if(word == null)
 			throw new WrongTokenFormatException("words should not be null");
 
@@ -31,5 +31,10 @@ public class Token{
 		}
 
 		token = word;
+	}
+
+
+	public String getToken(){
+		return token;
 	}
 }

### 2014-10-16 src/test/java/com/aic/preprocessing/TokenTypeTest.java

@@ -1,0 +1,21 @@
+import org.junit.* ;
+import static org.junit.Assert.* ;
+
+import com.aic.preprocessing.*;
+
+public class TokenTypeTest {
+
+   public void test_TokenConstuctor() {
+
+   	try{
+   		Token tt = new Token("#test");
+     	assertTrue(tt.getToken().equals("test")) ;
+     } catch(WrongTokenFormatException e){
+
+     }
+   }
+
+   public void test_True() {
+      assertTrue(false) ;
+   }
+}

### 2014-10-16 src/main/java/com/aic/preprocessing/Test.java
test fixed

@@ -1,10 +1,0 @@
-package com.aic.preprocessing;
-
-/*
-	Testklasse
-*/
-public class Test {
-	public static void main(String[] args){
-		System.out.println("Hello World!");
-	}
-}

### 2014-10-16 src/test/java/com/aic/preprocessing/TokenTypeTest.java

@@ -1,21 +1,0 @@
-import org.junit.* ;
-import static org.junit.Assert.* ;
-
-import com.aic.preprocessing.*;
-
-public class TokenTypeTest {
-
-   public void test_TokenConstuctor() {
-
-   	try{
-   		Token tt = new Token("#test");
-     	assertTrue(tt.getToken().equals("test")) ;
-     } catch(WrongTokenFormatException e){
-
-     }
-   }
-
-   public void test_True() {
-      assertTrue(false) ;
-   }
-}

### 2014-11-03 src/main/java/com/aic/components/Token.java
urlremove fixed and cleanup.

@@ -1,59 +1,0 @@
-package com.aic.components;
-
-import java.io.Serializable;
-
-import com.aic.preprocessing.*;
-
-public class Token implements Serializable{
-	private static final long serialVersionUID = -2290044716672034421L;
-
-	TokenType type;
-	String token;
-	String value;
-
-	// TODO: minimal length?
-	public Token(String word) throws WrongTokenFormatException{
-		if(word == null)
-			throw new WrongTokenFormatException("words should not be null");
-
-		if(word.length() < 1)
-			throw new WrongTokenFormatException("words should have at least one character");
-
-		if(word.contains(" "))
-			throw new WrongTokenFormatException("words should not contain space");
-
-		// TODO: Satzzeichen
-		switch(word.charAt(0)){
-			case '#':
-				type = TokenType.TAG;
-				value = word.substring(1);
-				break;
-			case '@':
-				type = TokenType.MENTIONING;
-				value = word.substring(1);
-				break;
-			default:
-				type = TokenType.WORD;
-				value = word;
-		}
-
-		token = word;
-	}
-
-
-	public String getToken(){
-		return token;
-	}
-
-	public String getValue(){
-		return value;
-	}
-
-	public void setValue(String value){
-		this.value = value;
-	}
-
-	public TokenType getType(){
-		return type;
-	}
-}

### 2014-11-03 src/main/java/com/aic/components/TwitterStatus.java

@@ -1,17 +1,43 @@
 package com.aic.components;
 
-import edu.stanford.nlp.trees.Tree;
-import twitter4j.*;
+import twitter4j.Place;
+import twitter4j.Status;
 
-import java.util.*;
 import java.io.Serializable;
+import java.util.Date;
+import java.util.List;
 
 public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 {
 	private static final long serialVersionUID = 7526472295654436147L;
-	private List<Tree> token;
+	private List<TaggedTwitterWord> content;
 	private Date timestamp;
-	private int favouriteCount;
+
+    public int getRetweetCount() {
+        return retweetCount;
+    }
+
+    public void setRetweetCount(int retweetCount) {
+        this.retweetCount = retweetCount;
+    }
+
+    public int getFavouriteCount() {
+        return favouriteCount;
+    }
+
+    public void setFavouriteCount(int favouriteCount) {
+        this.favouriteCount = favouriteCount;
+    }
+
+    public Place getLocation() {
+        return location;
+    }
+
+    public void setLocation(Place location) {
+        this.location = location;
+    }
+
+    private int favouriteCount;
 	private int retweetCount;
 	private Place location;
 	private String username;
@@ -26,7 +52,7 @@ public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 			username = twitter4jstatus.getUser().getScreenName();
 			id = twitter4jstatus.getId();
 			
-			token = com.aic.preprocessing.TweetProcess.preprocess(twitter4jstatus.getText());
+			content = com.aic.preprocessing.TweetProcess.preprocess(twitter4jstatus.getText());
 		}
 
 	/**
@@ -41,18 +67,18 @@ public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 			this.username = username;
 			this.id = -1;
 
-			token = com.aic.preprocessing.TweetProcess.preprocess(text);
+			content = com.aic.preprocessing.TweetProcess.preprocess(text);
 		}
 
 	public String toString()
 	{
-		return timestamp.toString() + " [" + username + "] " + join(token);
+		return timestamp.toString() + " [" + username + "] " + join(content);
 	}
 
-	private static String join(List<Tree> treeList)
+	private static String join(List<TaggedTwitterWord> treeList)
 	{
 		StringBuilder sb = new StringBuilder();
-		for (Tree t: treeList)
+		for (TaggedTwitterWord t: treeList)
 		{
 			sb.append(t);
 		}

### 2014-11-03 src/main/java/com/aic/preprocessing/TweetProcess.java

@@ -7,7 +7,6 @@ import edu.stanford.nlp.parser.lexparser.LexicalizedParser;
 import edu.stanford.nlp.process.DocumentPreprocessor;
 import edu.stanford.nlp.tagger.maxent.MaxentTagger;
 import edu.stanford.nlp.trees.Tree;
-import edu.stanford.nlp.util.CoreMap;
 import edu.stanford.nlp.util.Filter;
 
 import java.io.StringReader;
@@ -20,12 +19,12 @@ public class TweetProcess {
 
 
     /**
-     *
+     * 
      * @param input
      * @return
      */
-	public static List<Tree> preprocess(String input){
-        List<Tree> trees = new ArrayList<Tree>();
+	public static List<TaggedTwitterWord> preprocess(String input){
+        List<TaggedTwitterWord> token = new ArrayList<TaggedTwitterWord>();
 
         String preprocessed_string = removeURLs(removeRepeatedChars(input));
 
@@ -36,10 +35,13 @@ public class TweetProcess {
         for (List<HasWord> sentence : tokenizer) {
             List<TaggedWord> tagged = tagger.tagSentence(sentence);
             Tree tree = parser.apply(TaggedTwitterWord.fromTaggedWordList(tagged));
-            trees.add(filter(tree));
+
+            //convert tree to list
+            List<TaggedTwitterWord> ttwl = filter(tree).yieldHasWord();
+            token.addAll(ttwl);
         }
 
-        return trees;
+        return token;
 	}
 
     /**
@@ -90,8 +92,8 @@ public class TweetProcess {
 	* Remove URLS
 	*/
 	public static String removeURLs(String token){
-		final String regex = "(?:^|\\s)(https?|ftp|file)://[-a-zA-Z0-9+&@#/%?=~_|!:,.;]*[-a-zA-Z0-9+&@#/%=~_|]";
+		final String regex = "(https?|ftp|file)://[-a-zA-Z0-9+&@#/%?=~_|!:,.;]*[-a-zA-Z0-9+&@#/%=~_|]";
 		
-		return token.replace(regex,"");
+		return token.replaceAll(regex, "");
 	}
 }

### 2014-11-03 src/test/java/com/aic/components/TokenTest.java

@@ -1,45 +1,0 @@
-package com.aic.components;
-
-import org.junit.* ;
-import static org.junit.Assert.* ;
-
-import com.aic.preprocessing.*;
-import com.aic.components.*;
-
-public class TokenTest{
-
-	@Test
-	public void parseTagTokenConstuctor() {
-
-		try{
-			Token tt = new Token("#test");
-			assertTrue(tt.getValue().equals("test")) ;
-		} catch(WrongTokenFormatException e){
-			fail("should not throw WrongTokenFormatException");
-		}
-	}
-
-	@Test
-	public void parseMentioningTokenConstuctor() {
-
-		try{
-			Token tt = new Token("@somename");
-			assertTrue(tt.getValue().equals("somename"));
-			assertTrue(tt.getToken().equals("@somename"));
-		} catch(WrongTokenFormatException e){
-			fail("should not throw WrongTokenFormatException");
-		}
-	}
-
-	@Test
-	public void parseWordTokenConstuctor() {
-
-		try{
-			Token tt = new Token("someword");
-			assertTrue(tt.getValue().equals("someword"));
-			assertTrue(tt.getToken().equals("someword"));
-		} catch(WrongTokenFormatException e){
-			fail("should not throw WrongTokenFormatException");
-		}
-	}
-}

### 2014-11-03 src/test/java/com/aic/preprocessing/TweetProcessTest.java

@@ -9,6 +9,7 @@ public class TweetProcessTest{
 
 	@Test
 	public void removeValidURL() {
+        System.out.println("http://orf.at: " + TweetProcess.removeURLs("http://orf.at"));
     	assertTrue(TweetProcess.removeURLs("http://orf.at").isEmpty());
         assertEquals(TweetProcess.removeURLs("hey http://orf.at"), "hey ");
         assertEquals(TweetProcess.removeURLs("hey du"), "hey du");

### 2014-11-03 src/main/java/com/aic/components/TaggedTwitterWord.java
fixed testcase and taggedtwitterword factory

@@ -25,22 +25,24 @@ public class TaggedTwitterWord extends TaggedWord{
     }
 
     private static TaggedTwitterWord fromTaggedWord(TaggedWord tw) {
-
         TaggedTwitterWord ttw = new TaggedTwitterWord();
+        ttw.setTag(tw.tag());
+
 
         switch(tw.toString().charAt(0)){
             case '@':
                 ttw.type = TokenType.MENTIONING;
-                ttw.setTag(tw.toString().substring(1));
+                ttw.setWord(tw.word().substring(1));
                 break;
             case '#':
                 ttw.type = TokenType.TAG;
-                ttw.setTag(tw.toString().substring(1));
+                ttw.setWord(tw.word().substring(1));
                 break;
             default:
                 ttw.type = TokenType.WORD;
-                ttw.setTag(tw.toString());
+                ttw.setWord(tw.word());
         }
+
         return ttw;
     }
 

### 2014-11-03 src/main/java/com/aic/preprocessing/TweetProcess.java

@@ -19,7 +19,7 @@ public class TweetProcess {
 
 
     /**
-     * 
+     *
      * @param input
      * @return
      */

### 2014-11-03 src/test/java/com/aic/ExampleTest.java

@@ -1,25 +1,21 @@
 package com.aic;
 
-import com.aic.components.TaggedTwitterWord;
+import edu.stanford.nlp.ling.CoreAnnotations;
+import edu.stanford.nlp.ling.HasWord;
+import edu.stanford.nlp.ling.TaggedWord;
 import edu.stanford.nlp.neural.rnn.RNNCoreAnnotations;
 import edu.stanford.nlp.parser.lexparser.LexicalizedParser;
-import edu.stanford.nlp.parser.shiftreduce.ShiftReduceParser;
+import edu.stanford.nlp.pipeline.Annotation;
+import edu.stanford.nlp.pipeline.StanfordCoreNLP;
 import edu.stanford.nlp.process.DocumentPreprocessor;
 import edu.stanford.nlp.sentiment.SentimentCoreAnnotations;
-import edu.stanford.nlp.tagger.common.Tagger;
 import edu.stanford.nlp.tagger.maxent.MaxentTagger;
-import edu.stanford.nlp.tagger.maxent.TestSentence;
 import edu.stanford.nlp.trees.Tree;
 import edu.stanford.nlp.trees.TreePrint;
+import edu.stanford.nlp.util.CoreMap;
 import org.junit.Test;
 
-import edu.stanford.nlp.ling.*;
-import edu.stanford.nlp.pipeline.*;
-import edu.stanford.nlp.util.*;
-
-
 import java.io.StringReader;
-import java.util.ArrayList;
 import java.util.List;
 import java.util.Properties;
 
@@ -67,8 +63,9 @@ public class ExampleTest {
         for (List<HasWord> sentence : tokenizer) {
 
             List<TaggedWord> tagged = tagger.tagSentence(sentence);
+            //TaggedTwitterWord.fromTaggedWordList(tagged)
+            Tree tree = parser.apply(tagged);
 
-            Tree tree = parser.apply(TaggedTwitterWord.fromTaggedWordList(tagged));
             //System.out.println(tree);
             new TreePrint("penn,typedDependenciesCollapsed").printTree(tree);
         }

### 2014-11-03 src/test/java/com/aic/preprocessing/TweetProcessTest.java

@@ -1,6 +1,17 @@
 package com.aic.preprocessing;
 
+import com.aic.components.TaggedTwitterWord;
+import edu.stanford.nlp.ling.HasWord;
+import edu.stanford.nlp.ling.TaggedWord;
+import edu.stanford.nlp.parser.lexparser.LexicalizedParser;
+import edu.stanford.nlp.process.DocumentPreprocessor;
+import edu.stanford.nlp.tagger.maxent.MaxentTagger;
+import edu.stanford.nlp.trees.Tree;
+import edu.stanford.nlp.trees.TreePrint;
 import org.junit.Test;
+
+import java.io.StringReader;
+import java.util.List;
 
 import static org.junit.Assert.assertEquals;
 import static org.junit.Assert.assertTrue;
@@ -28,5 +39,32 @@ public class TweetProcessTest{
         assertEquals(TweetProcess.removeRepeatedChars("thiis"), "thiis");
         assertEquals(TweetProcess.removeRepeatedChars("thisss"), "thisss");
 	}
+
+
+
+    @Test
+    public void parseTweet() {
+        final String PCG_MODEL = "edu/stanford/nlp/models/lexparser/englishPCFG.ser.gz";
+        //String modelPath = "edu/stanford/nlp/models/srparser/englishSR.ser.gz";
+
+        String taggerPath = "edu/stanford/nlp/models/pos-tagger/english-left3words/english-left3words-distsim.tagger";
+
+        String text = "My dog likes to shake his stuffed chickadee toy. some #tags";
+
+        final MaxentTagger tagger = new MaxentTagger(taggerPath);
+        //ShiftReduceParser model = ShiftReduceParser.loadModel(modelPath);
+        LexicalizedParser parser = LexicalizedParser.loadModel(PCG_MODEL);
+
+        DocumentPreprocessor tokenizer = new DocumentPreprocessor(new StringReader(text));
+
+        for (List<HasWord> sentence : tokenizer) {
+
+            List<TaggedWord> tagged = tagger.tagSentence(sentence);
+            Tree tree = parser.apply(TaggedTwitterWord.fromTaggedWordList(tagged));
+
+            //System.out.println(tree);
+            new TreePrint("penn,typedDependenciesCollapsed").printTree(tree);
+        }
+    }
 
 }

### 2014-11-03 src/main/java/com/aic/components/TaggedTwitterWord.java
tree to list fixed and testcase added

@@ -2,6 +2,7 @@ package com.aic.components;
 
 import edu.stanford.nlp.ling.HasWord;
 import edu.stanford.nlp.ling.TaggedWord;
+import edu.stanford.nlp.trees.Tree;
 
 import java.util.ArrayList;
 import java.util.List;
@@ -12,6 +13,17 @@ import java.util.List;
 public class TaggedTwitterWord extends TaggedWord{
     private TokenType type;
 
+    public static List<TaggedTwitterWord> fromTree(Tree t){
+        List<TaggedTwitterWord> result = new ArrayList<>();
+
+        // Puntigam würd mich für das killen ...
+        for(HasWord ttw: t.yieldHasWord()){
+            if(ttw instanceof TaggedTwitterWord)
+                result.add((TaggedTwitterWord) ttw);
+        }
+
+        return result;
+    }
 
     public static List<? extends HasWord> fromTaggedWordList(List<TaggedWord> tagged) {
         List<TaggedTwitterWord> result = new ArrayList<TaggedTwitterWord>();

### 2014-11-03 src/main/java/com/aic/fetch/Cache.java

@@ -8,13 +8,27 @@ import com.aic.components.*;
 
 import java.nio.file.*;
 
+import static java.io.File.createTempFile;
+
 /**
  * @todo implement
  */
 
 public class Cache
 {
-	public static final File path = new File("tmp" + File.separator + "cache");
+    public static final Path path = getTempDirectory();
+
+    private static Path getTempDirectory(){
+        Path result = null;
+
+        try {
+            result = Files.createTempDirectory(null).toAbsolutePath();
+        } catch (IOException e) {
+            e.printStackTrace();
+        }
+
+        return result;
+    }
 
 	/**
 	 * loads a list of already cached datasets cuts overlapping parts that are
@@ -51,14 +65,13 @@ public class Cache
 		return result;
 	}
 
-	/**
-	 * serializes and stores the given tweet list.
-	 * 
-	 * @param end
-	 * @param start
-	 */
-	public static File store(TwitterStatusList tweets)
-	{
+    /**
+     *
+     * @param tweets
+     * @return
+     * @throws IOException
+     */
+	public static File store(TwitterStatusList tweets) {
 		Date start = tweets.getStart();
 		Date end = tweets.getEnd();
 		System.out.println("Store: start: " +start + ", end: "+end);
@@ -67,8 +80,13 @@ public class Cache
 			start = tweets.getStart();
 			end = tweets.getEnd();
 		}
-		File outputfile = new File(path + File.separator + tweets.getKeyword() + "_" + start.getTime() + "_" + end.getTime());
-		outputfile.getParentFile().mkdirs();
+        File outputfile = null;
+        try {
+            outputfile = File.createTempFile(File.separator + tweets.getKeyword() + "_" + start.getTime() + "_" + end.getTime(), ".tmp");
+        } catch (IOException e) {
+            e.printStackTrace();
+        }
+        //outputfile.getParentFile().mkdirs();
 
 		try
 		{
@@ -132,7 +150,10 @@ public class Cache
 	// TODO javadoc	
 	public static File[] getFilePaths(final String keyword)
 	{
-		File dir = new File(path.getPath());
+		File dir = new File(path.toString());
+
+
+
 		File[] files = dir.listFiles(new FilenameFilter()
 		{
 			@Override
@@ -158,13 +179,13 @@ public class Cache
 
 	public static void clear()
 	{
-		clearDirectory(path);
+		clearDirectory(path.toString());
 	}
 
[…]

### 2014-11-03 src/main/java/com/aic/preprocessing/TweetProcess.java

@@ -37,12 +37,13 @@ public class TweetProcess {
             Tree tree = parser.apply(TaggedTwitterWord.fromTaggedWordList(tagged));
 
             //convert tree to list
-            List<TaggedTwitterWord> ttwl = filter(tree).yieldHasWord();
+            List<TaggedTwitterWord> ttwl = TaggedTwitterWord.fromTree(filter(tree));
             token.addAll(ttwl);
         }
 
         return token;
 	}
+
 
     /**
      * filter tree
@@ -56,10 +57,15 @@ public class TweetProcess {
 
             public boolean accept(Tree t) {
                 //example. removes foreign words
-                return ! t.label().value().equals("FW");
+                return notForeignWord(t);
+            }
+
+            public boolean notForeignWord(Tree t) {
+                return !t.label().value().equals("FW");
             }
 
         };
+
 
 
 

### 2014-11-03 src/test/java/com/aic/fetch/CacheTest.java

@@ -17,12 +17,14 @@ public class CacheTest{
 	public void fileCreated() {
 		Cache.clear();
 
-		TwitterStatusList tweetlist = new TwitterStatusList("microsoft");
 		Date timestamp = new Date();
+        TwitterStatusList tweetlist = new TwitterStatusList("microsoft");
 		tweetlist.add(new TwitterStatus(timestamp, "inkrement", "some #fancy tweet @twitter"));
 
+        System.out.println("tweetlist to store: " + tweetlist);
 		Cache.store(tweetlist);
 
+        System.out.println("Pfad: " + Cache.path);
 		File file = new File(Cache.path + File.separator + "microsoft_" + timestamp.getTime() + "_" + timestamp.getTime());
 
 		System.out.println("fileCreated path: " + file);
@@ -56,7 +58,7 @@ public class CacheTest{
 
 	@Test
 	public void clearCache() {
-		String filepath = Cache.path.getPath() + File.separator + "somerandomfile";
+		String filepath = Cache.path.toString() + File.separator + "somerandomfile";
 		System.out.println("filepath: " + filepath);
 
 		File f = new File(filepath);

### 2014-11-03 src/test/java/com/aic/preprocessing/TweetProcessTest.java

@@ -11,6 +11,7 @@ import edu.stanford.nlp.trees.TreePrint;
 import org.junit.Test;
 
 import java.io.StringReader;
+import java.util.Iterator;
 import java.util.List;
 
 import static org.junit.Assert.assertEquals;
@@ -63,8 +64,48 @@ public class TweetProcessTest{
             Tree tree = parser.apply(TaggedTwitterWord.fromTaggedWordList(tagged));
 
             //System.out.println(tree);
-            new TreePrint("penn,typedDependenciesCollapsed").printTree(tree);
+            //new TreePrint("penn,typedDependenciesCollapsed").printTree(tree);
         }
+    }
+
+    @Test
+    public void treeToList() {
+        final String PCG_MODEL = "edu/stanford/nlp/models/lexparser/englishPCFG.ser.gz";
+        //String modelPath = "edu/stanford/nlp/models/srparser/englishSR.ser.gz";
+
+        String taggerPath = "edu/stanford/nlp/models/pos-tagger/english-left3words/english-left3words-distsim.tagger";
+
+        String text = "My dog likes to shake his stuffed chickadee toy";
+
+        final MaxentTagger tagger = new MaxentTagger(taggerPath);
+        //ShiftReduceParser model = ShiftReduceParser.loadModel(modelPath);
+        LexicalizedParser parser = LexicalizedParser.loadModel(PCG_MODEL);
+
+        DocumentPreprocessor tokenizer = new DocumentPreprocessor(new StringReader(text));
+
+        Iterator<List<HasWord>> i = tokenizer.iterator();
+        //assert elements
+        assertTrue(i.hasNext());
+
+        List<TaggedTwitterWord> taggedwords = null;
+
+        System.out.println("start iterate sentences: " + tokenizer.toString());
+
+        while (i.hasNext()) {
+            List<HasWord> sentence = i.next();
+            System.out.println("Sentence: " + sentence);
+
+            List<TaggedWord> tagged = tagger.tagSentence(sentence);
+            Tree tree = parser.apply(TaggedTwitterWord.fromTaggedWordList(tagged));
+
+            taggedwords = TaggedTwitterWord.fromTree(tree);
+
+            System.out.println("list: " + taggedwords);
+        }
+
+        assertEquals(taggedwords.size(), 9);
+
+
     }
 
 }

### 2014-11-03 src/main/java/com/aic/preprocessing/TweetProcess.java
filter added

@@ -53,13 +53,81 @@ public class TweetProcess {
 	public static Tree filter(Tree tree){
         Tree PrunedTree ;
 
+        /**
+         * CC - Coordinating conjunction
+         CD - Cardinal number
+         DT - Determiner
+         EX - Existential there
+         FW - Foreign word
+         IN - Preposition or subordinating conjunction
+         LS - List item marker
+         PDT - Predeterminer
+         POS - Possessive ending
+         PRP - Personal pronoun
+         PRP$ - Possessive pronoun (prolog version PRP-S)
+         TO - to
+         WDT - Wh-determiner
+         WP - Wh-pronoun
+         WP$ - Possessive wh-pronoun (prolog version WP-S)
+         WRB - Wh-adverb
+         */
+
         Filter<Tree> f = new Filter<Tree>() {
 
             public boolean accept(Tree t) {
                 //example. removes foreign words
-                return notForeignWord(t);
+                return notForeignWord(t) || notCardinalNumber(t) || notCoordinationConjungtion(t) ||
+                        notDeterminer(t) || notExtentionalThere(t) || notListItemMarker(t) ||
+                        notPersonalPronoun(t) || notPossessiveEnding(t) || notPossessivePronoun(t) ||
+                        notPossessiveWhPronoun(t) || notPredeterminer(t) || notPreposition(t) ||
+                        notTo(t) || notWhDeterminer(t) || notWhPronoun(t) ||
+                        notWhAdverb(t);
             }
-
+            public boolean notCoordinationConjungtion(Tree t){
+                return !t.label().value().equals("CC");
+            }
+            public boolean notCardinalNumber(Tree t){
+                return !t.label().value().equals("CD");
+            }
+            public boolean notDeterminer(Tree t){
+                return !t.label().value().equals("DT");
+            }
+            public boolean notExtentionalThere(Tree t){
+                return !t.label().value().equals("EX");
+            }
+            public boolean notPreposition(Tree t){
+                return !t.label().value().equals("IN");
+            }
+            public boolean notListItemMarker(Tree t){
+                return !t.label().value().equals("LS");
+            }
+            public boolean notPredeterminer(Tree t){
+                return !t.label().value().equals("PDT");
+            }
+            public boolean notPossessiveEnding(Tree t){
+                return !t.label().value().equals("POS");
+            }
+            public boolean notPersonalPronoun(Tree t){
+                return !t.label().value().equals("PRP");
+            }
+            public boolean notPossessivePronoun(Tree t){
[…]

### 2014-11-04 paper/chapters/1_introduction.tex
paper template cleanup

\section{Introduction}

try to cite someone \autocite{Kouloumpis2011}

### 2014-11-04 paper/paper.tex
makefile updated
paper template cleanup

@@
 
+%% set up bibliography
+\usepackage[backend=bibtex,doi=false,isbn=false,url=false]{biblatex}
+\bibliography{biblio}  % sigproc.bib is the name of the Bibliography in this case
+%\bibliographystyle{acm}
+
 \begin{document}
-%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
 
@@
 \begin{abstract}
-This paper provides a sample of a \LaTeX\ document which conforms,
-somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
 
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
 \end{abstract}
@@
 
-\section{Introduction}
-The \textit{proceedings} are the records of a conference.
-ACM seeks to give these conference by-products a uniform,
-high-quality appearance.  To do this, ACM has some rigid
-requirements for the format of the proceedings documents: there
-is a specified format (balanced  double columns), a specified
-set of fonts (Arial or Helvetica and Times Roman) in
-certain specified sizes (for instance, 9 point for body copy),
-a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
-the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
-and (1.9 cm [.75"]) left and right; specified column width
-(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).
-
-The good news is, with only a handful of manual
-settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
-and {\texttt{\char'134 alignauthor}} commands, you have
-already used; another, {\texttt{\char'134 balancecolumns}}, will
-be used in your very last run of \LaTeX\ to ensure
-balanced column heights on the last page.}, the \LaTeX\ document
-class file handles all of this for you.
-
-The remainder of this document is concerned with showing, in
-the context of an ``actual'' document, the \LaTeX\ commands
-specifically available for denoting the structure of a
-proceedings paper, rather than with giving rigorous descriptions
-or explanations of such commands.
-
-\section{The {\secit Body} of The Paper}
-Typically, the body of a paper is organized
-into a hierarchical structure, with numbered or unnumbered
-headings for sections, subsections, sub-subsections, and even
-smaller sections.  The command \texttt{{\char'134}section} that
-precedes this paragraph is part of such a
-hierarchy.\footnote{This is the second footnote.  It
-starts a series of three footnotes that add nothing
-informational, but just give an idea of how footnotes work
-and look. It is a wordy one, just so you see
-how a longish one plays out.} \LaTeX\ handles the numbering
-and placement of these headings for you, when you use
-the appropriate heading commands around the titles
-of the headings.  If you want a sub-subsection or
-smaller part to be unnumbered in your output, simply append an
-asterisk to the command name.  Examples of both
-numbered and unnumbered headings will appear throughout the
-balance of this sample document.
-
-Because the entire article is contained in
-the \textbf{document} environment, you can indicate the
-start of a new paragraph with a blank line in your
-input file; that is why this sentence forms a separate paragraph.
-
-\subsection{Type Changes and {\subsecit Special} Characters}
-We have already seen several typeface changes in this sample.  You
-can indicate italicized words or phrases in your text with
-the command \texttt{{\char'134}textit}; emboldening with the
-command \texttt{{\char'134}textbf}
-and typewriter-style (for instance, for computer code) with
-\texttt{{\char'134}texttt}.  But remember, you do not
-have to indicate typestyle changes when such changes are
-part of the \textit{structural} elements of your
-article; for instance, the heading of this subsection will
-be in a sans serif\footnote{A third footnote, here.
-Let's make this a rather short one to
-see how it looks.} typeface, but that is handled by the
-document class file. Take care with the use
-of\footnote{A fourth, and last, footnote.}
-the curly braces in typeface changes; they mark
-the beginning and end of
-the text that is to be in the different typeface.
-
-You can use whatever symbols, accented characters, or
-non-English characters you need anywhere in your document;
-you can find a complete list of what is
-available in the \textit{\LaTeX\
-User's Guide}\cite{Lamport:LaTeX}.
-
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
-
-\subsubsection{Inline (In-text) Equations}
-A formula that appears in the running text is called an
-inline or in-text formula.  It is produced by the
-\textbf{math} environment, which can be
-invoked with the usual \texttt{{\char'134}begin. . .{\char'134}end}
-construction or with the short form \texttt{\$. . .\$}. You
-can use any of the symbols and structures,
-from $\alpha$ to $\omega$, available in
-\LaTeX\cite{Lamport:LaTeX}; this section will simply show a
-few examples of in-text equations in context. Notice how
-this equation: \begin{math}\lim_{n\rightarrow \infty}x=0\end{math},
-set here in in-line math style, looks slightly different when
-set in display style.  (See next section).
-
-\subsubsection{Display Equations}
-A numbered display equation -- one set off by vertical space
-from the text and centered horizontally -- is produced
-by the \textbf{equation} environment. An unnumbered display
-equation is produced by the \textbf{displaymath} environment.
-
-Again, in either environment, you can use any of the symbols
-and structures available in \LaTeX; this section will just
-give a couple of examples of display equations in context.
-First, consider the equation, shown as an inline equation above:
-\begin{equation}\lim_{n\rightarrow \infty}x=0\end{equation}
-Notice how it is formatted somewhat differently in
-the \textbf{displaymath}
-environment.  Now, we'll enter an unnumbered equation:
-\begin{displaymath}\sum_{i=0}^{\infty} x + 1\end{displaymath}
-and follow it with another numbered equation:
-\begin{equation}\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f\end{equation}
-just to demonstrate \LaTeX's able handling of numbering.
-
-\subsection{Citations}
-Citations to articles \cite{bowman:reasoning,
-clark:pct, braams:babel, herlihy:methodology},
-conference proceedings \cite{clark:pct} or
-books \cite{salas:calculus, Lamport:LaTeX} listed
-in the Bibliography section of your
-article will occur throughout the text of your article.
-You should use BibTeX to automatically produce this bibliography;
-you simply need to insert one of several citation commands with
-a key of the item cited in the proper location in
-the \texttt{.tex} file \cite{Lamport:LaTeX}.
-The key is a short reference you invent to uniquely
-identify each work; in this sample document, the key is
-the first author's surname and a
-word from the title.  This identifying key is included
-with each item in the \texttt{.bib} file for your article.
-
-The details of the construction of the \texttt{.bib} file
-are beyond the scope of this sample document, but more
-information can be found in the \textit{Author's Guide},
-and exhaustive details in the \textit{\LaTeX\ User's
-Guide}\cite{Lamport:LaTeX}.
-
-This article shows only the plainest form
-of the citation command, using \texttt{{\char'134}cite}.
-This is what is stipulated in the SIGS style specifications.
-No other citation format is endorsed or supported.
-
-\subsection{Tables}
-Because tables cannot be split across pages, the best
-placement for them is typically the top of the page
-nearest their initial cite.  To
-ensure this proper ``floating'' placement of tables, use the
-environment \textbf{table} to enclose the table's contents and
-the table caption.  The contents of the table itself must go
-in the \textbf{tabular} environment, to
-be aligned properly in rows and columns, with the desired
-horizontal and vertical rules.  Again, detailed instructions
-on \textbf{tabular} material
-is found in the \textit{\LaTeX\ User's Guide}.
-
-Immediately following this sentence is the point at which
-Table 1 is included in the input file; compare the
-placement of the table here with the table in the printed
-dvi output of this document.
-
-\begin{table}
-\centering
-\caption{Frequency of Special Characters}
-\begin{tabular}{|c|c|l|} \hline
-Non-English or Math&Frequency&Comments\\ \hline
-\O & 1 in 1,000& For Swedish names\\ \hline
-$\pi$ & 1 in 5& Common in math\\ \hline
-\$ & 4 in 5 & Used in business\\ \hline
-$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
-\hline\end{tabular}
-\end{table}
-
-To set a wider table, which takes up the whole width of
-the page's live area, use the environment
-\textbf{table*} to enclose the table's contents and
-the table caption.  As with a single-column table, this wide
-table will ``float" to a location deemed more desirable.
-Immediately following this sentence is the point at which
-Table 2 is included in the input file; again, it is
-instructive to compare the placement of the
-table here with the table in the printed dvi
-output of this document.
-
-\begin{table*}
-\centering
-\caption{Some Typical Commands}
-\begin{tabular}{|c|c|l|} \hline
-Command&A Number&Comments\\ \hline
-\texttt{{\char'134}alignauthor} & 100& Author alignment\\ \hline
-\texttt{{\char'134}numberofauthors}& 200& Author enumeration\\ \hline
-\texttt{{\char'134}table}& 300 & For tables\\ \hline
-\texttt{{\char'134}table*}& 400& For wider tables\\ \hline\end{tabular}
-\end{table*}
-% end the environment with {table*}, NOTE not {table}!
-
-\subsection{Figures}
-Like tables, figures cannot be split across pages; the
-best placement for them
-is typically the top or the bottom of the page nearest
-their initial cite.  To ensure this proper ``floating'' placement
-of figures, use the environment
-\textbf{figure} to enclose the figure and its caption.
-
-This sample document contains examples of \textbf{.eps}
-and \textbf{.ps} files to be displayable with \LaTeX.  More
-details on each of these is found in the \textit{Author's Guide}.
-
-%\begin{figure}
-%centering
-%\epsfig{file=fly.eps}
-%\caption{A sample black and white graphic (.eps format).}
-%\end{figure}
-
-%\begin{figure}
-%\centering
-%\epsfig{file=fly.eps, height=1in, width=1in}
-%\caption{A sample black and white graphic (.eps format)
-%that has been resized with the \texttt{epsfig} command.}
-%\end{figure}
-
-As was the case with tables, you may want a figure
-that spans two columns.  To do this, and still to
-ensure proper ``floating'' placement of tables, use the environment
-\textbf{figure*} to enclose the figure and its caption.
-and don't forget to end the environment with
-{figure*}, not {figure}!
-
-Note that either {\textbf{.ps}} or {\textbf{.eps}} formats are
-used; use
-the \texttt{{\char'134}epsfig} or \texttt{{\char'134}psfig}
-commands as appropriate for the different file types.
-
-\subsection{Theorem-like Constructs}
-Other common constructs that may occur in your article are
-the forms for logical constructs like theorems, axioms,
-corollaries and proofs.  There are
-two forms, one produced by the
-command \texttt{{\char'134}newtheorem} and the
-other by the command \texttt{{\char'134}newdef}; perhaps
-the clearest and easiest way to distinguish them is
-to compare the two in the output of this sample document:
-
-This uses the \textbf{theorem} environment, created by
-the\linebreak\texttt{{\char'134}newtheorem} command:
-\newtheorem{theorem}{Theorem}
-\begin{theorem}
-Let $f$ be continuous on $[a,b]$.  If $G$ is
-an antiderivative for $f$ on $[a,b]$, then
-\begin{displaymath}\int^b_af(t)dt = G(b) - G(a).\end{displaymath}
-\end{theorem}
-
-The other uses the \textbf{definition} environment, created
-by the \texttt{{\char'134}newdef} command:
-\newdef{definition}{Definition}
-\begin{definition}
-If $z$ is irrational, then by $e^z$ we mean the
-unique number which has
-logarithm $z$: \begin{displaymath}{\log e^z = z}\end{displaymath}
-\end{definition}
-
-Two lists of constructs that use one of these
-forms is given in the
-\textit{Author's  Guidelines}.
-
-There is one other similar construct environment, which is
-already set up
-for you; i.e. you must \textit{not} use
-a \texttt{{\char'134}newdef} command to
-create it: the \textbf{proof} environment.  Here
-is a example of its use:
-\begin{proof}
-Suppose on the contrary there exists a real number $L$ such that
-\begin{displaymath}
-\lim_{x\rightarrow\infty} \frac{f(x)}{g(x)} = L.
-\end{displaymath}
-Then
-\begin{displaymath}
-l=\lim_{x\rightarrow c} f(x)
-= \lim_{x\rightarrow c}
-\left[ g{x} \cdot \frac{f(x)}{g(x)} \right ]
-= \lim_{x\rightarrow c} g(x) \cdot \lim_{x\rightarrow c}
-\frac{f(x)}{g(x)} = 0\cdot L = 0,
-\end{displaymath}
-which contradicts our assumption that $l\neq 0$.
-\end{proof}
-
-Complete rules about using these environments and using the
-two different creation commands are in the
-\textit{Author's Guide}; please consult it for more
-detailed instructions.  If you need to use another construct,
-not listed therein, which you want to have the same
-formatting as the Theorem
-or the Definition\cite{salas:calculus} shown above,
-use the \texttt{{\char'134}newtheorem} or the
-\texttt{{\char'134}newdef} command,
-respectively, to create it.
-
-\subsection*{A {\secit Caveat} for the \TeX\ Expert}
-Because you have just been given permission to
-use the \texttt{{\char'134}newdef} command to create a
-new form, you might think you can
-use \TeX's \texttt{{\char'134}def} to create a
-new command: \textit{Please refrain from doing this!}
-Remember that your \LaTeX\ source code is primarily intended
-to create camera-ready copy, but may be converted
-to other forms -- e.g. HTML. If you inadvertently omit
-some or all of the \texttt{{\char'134}def}s recompilation will
-be, to say the least, problematic.
-
-\section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
+\input{chapters/1_introduction.tex}
+\input{chapters/2_methods.tex}
+\input{chapters/3_conclusions.tex}
 
@@
 % produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+
 % You must have a proper ".bib" file
@@
 \section{Headings in Appendices}
-The rules about hierarchical headings discussed above for
-the body of the article are different in the appendices.
-In the \textbf{appendix} environment, the command
-\textbf{section} is used to
-indicate the start of each Appendix, with alphabetic order
-designation (i.e. the first is A, the second B, etc.) and
-a title (if you include one).  So, if you need
-hierarchical structure
-\textit{within} an Appendix, start with \textbf{subsection} as the
-highest level. Here is an outline of the body of this
-document in Appendix-appropriate form:
-\subsection{Introduction}
-\subsection{The Body of the Paper}
-\subsubsection{Type Changes and  Special Characters}
-\subsubsection{Math Equations}
-\paragraph{Inline (In-text) Equations}
-\paragraph{Display Equations}
-\subsubsection{Citations}
-\subsubsection{Tables}
-\subsubsection{Figures}
-\subsubsection{Theorem-like Constructs}
-\subsubsection*{A Caveat for the \TeX\ Expert}
-\subsection{Conclusions}
-\subsection{Acknowledgments}
-\subsection{Additional Authors}
-This section is inserted by \LaTeX; you do not insert it.
-You just add the names and information in the
-\texttt{{\char'134}additionalauthors} command at the start
-of the document.
-\subsection{References}
-Generated by bibtex from your ~.bib file.  Run latex,
-then bibtex, then latex twice (to resolve references)
-to create the ~.bbl file.  Insert that ~.bbl file into
-the .tex source file and comment out
-the command \texttt{{\char'134}thebibliography}.
-% This next section command marks the start of
-% Appendix B, and does not continue the present hierarchy
-\section{More Help for the Hardy}
-The sig-alternate.cls file itself is chock-full of succinct
-and helpful comments.  If you consider yourself a moderately
-experienced to expert user of \LaTeX, you may find reading
-it useful but please remember not to change it.
-%\balancecolumns % GM June 2007
-% That's all folks!
+
+\printbibliography
+
 \end{document}

### 2014-11-04 src/main/java/com/aic/components/TwitterStatus.java
CacheTest fixed - everything works except for Cache.clear()

@@ -7,6 +7,8 @@ import java.io.Serializable;
 import java.util.Date;
 import java.util.List;
 
+import com.aic.preprocessing.TweetProcess;
+
 public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 {
 	private static final long serialVersionUID = 7526472295654436147L;
@@ -52,7 +54,7 @@ public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 			username = twitter4jstatus.getUser().getScreenName();
 			id = twitter4jstatus.getId();
 			
-			content = com.aic.preprocessing.TweetProcess.preprocess(twitter4jstatus.getText());
+			content = TweetProcess.preprocess(twitter4jstatus.getText());
 		}
 
 	/**
@@ -67,7 +69,7 @@ public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 			this.username = username;
 			this.id = -1;
 
-			content = com.aic.preprocessing.TweetProcess.preprocess(text);
+			content = TweetProcess.preprocess(text);
 		}
 
 	public String toString()
@@ -105,5 +107,22 @@ public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 	public int compareTo(TwitterStatus other)
 	{
 		return timestamp.compareTo(other.getDate());
+	}
+
+	@Override
+	public int hashCode()
+	{
+		return (int) (id ^ (id >>> 32));
+	}
+
+	@Override
+	public boolean equals(Object obj)
+	{
+		if (this == obj) return true;
+		if (obj == null) return false;
+		if (getClass() != obj.getClass()) return false;
+		TwitterStatus other = (TwitterStatus) obj;
+		if (id != other.id) return false;
+		return true;
 	}
 }

### 2014-11-04 src/main/java/com/aic/components/TwitterStatusList.java

@@ -106,4 +106,45 @@ public class TwitterStatusList extends ArrayList<TwitterStatus> implements Compa
 		this.end = end;
 	}
 
+	@Override
+	public int hashCode()
+	{
+		final int prime = 31;
+		int result = super.hashCode();
+		result = prime * result + ((end == null) ? 0 : end.hashCode());
+		result = prime * result + ((keyword == null) ? 0 : keyword.hashCode());
+		result = prime * result + ((start == null) ? 0 : start.hashCode());
+		return result;
+	}
+
+	@Override
+	public boolean equals(Object obj)
+	{
+		System.out.println(this.toString() +"="+obj.toString());
+		if (this == obj) return true;
+		if (getClass() != obj.getClass()) return false;
+		TwitterStatusList other = (TwitterStatusList) obj;
+		if (end == null)
+		{
+			if (other.end != null) return false;
+		}
+		else if (!end.equals(other.end)) return false;
+		if (keyword == null)
+		{
+			if (other.keyword != null) return false;
+		}
+		else if (!keyword.equals(other.keyword)) return false;
+		if (start == null)
+		{
+			if (other.start != null) return false;
+		}
+		else if (!start.equals(other.start)) return false;
+		if (size() != other.size()) return false;
+		for (int i = 0; i < size(); i++)
+		{
+			if (!get(i).equals(other.get(i)))
+				return false;
+		}
+		return true;
+	}
 }

### 2014-11-04 src/main/java/com/aic/fetch/Cache.java

@@ -4,6 +4,7 @@ import java.util.Date;
 import java.util.List;
 import java.util.ArrayList;
 import java.io.*;
+
 import com.aic.components.*;
 
 import java.nio.file.*;
@@ -16,19 +17,7 @@ import static java.io.File.createTempFile;
 
 public class Cache
 {
-    public static final Path path = getTempDirectory();
-
-    private static Path getTempDirectory(){
-        Path result = null;
-
-        try {
-            result = Files.createTempDirectory(null).toAbsolutePath();
-        } catch (IOException e) {
-            e.printStackTrace();
-        }
-
-        return result;
-    }
+    public static final String PATH = "tmp" +  File.separator + "cache" + File.separator;
 
 	/**
 	 * loads a list of already cached datasets cuts overlapping parts that are
@@ -74,18 +63,13 @@ public class Cache
 	public static File store(TwitterStatusList tweets) {
 		Date start = tweets.getStart();
 		Date end = tweets.getEnd();
-		System.out.println("Store: start: " +start + ", end: "+end);
+		System.out.println("Store: start: " + start + ", end: "+end);
 		if (tweets.size() == Fetch.MAX_TWEETS)
 		{
 			start = tweets.getStart();
 			end = tweets.getEnd();
 		}
-        File outputfile = null;
-        try {
-            outputfile = File.createTempFile(File.separator + tweets.getKeyword() + "_" + start.getTime() + "_" + end.getTime(), ".tmp");
-        } catch (IOException e) {
-            e.printStackTrace();
-        }
+        File outputfile = new File(PATH + tweets.getKeyword() + "_" + start.getTime() + "_" + end.getTime()+ ".tmp");
         //outputfile.getParentFile().mkdirs();
 
 		try
@@ -99,11 +83,12 @@ public class Cache
 		}
 		catch (FileNotFoundException e)
 		{
-			System.err.println("could not find file: " + outputfile + " " + e.getMessage());
+			System.err.println("Could not find file: " + outputfile + " " + e.getMessage());
+			e.printStackTrace();
 		}
 		catch (IOException e)
 		{
-			System.err.println("could not write to file: " + outputfile + " " + e.getMessage());
+			System.err.println("Could not write to file: " + outputfile + " " + e.getMessage());
 			e.printStackTrace();
 		}
 
@@ -150,9 +135,7 @@ public class Cache
 	// TODO javadoc	
[…]

### 2014-11-04 src/test/java/com/aic/fetch/CacheTest.java

@@ -13,52 +13,60 @@ import java.io.IOException;
 
 public class CacheTest{
 
-	@Test
-	public void fileCreated() {
+	@Before
+	public void before() throws IOException
+	{
 		Cache.clear();
-
+	}
+	
+	@After
+	public void after() throws IOException
+	{
+		Cache.clear();
+	}
+	
+	@Test
+	public void fileCreated() throws IOException {
 		Date timestamp = new Date();
         TwitterStatusList tweetlist = new TwitterStatusList("microsoft");
 		tweetlist.add(new TwitterStatus(timestamp, "inkrement", "some #fancy tweet @twitter"));
+		tweetlist.setDates(timestamp, timestamp);
 
         System.out.println("tweetlist to store: " + tweetlist);
 		Cache.store(tweetlist);
 
-        System.out.println("Pfad: " + Cache.path);
-		File file = new File(Cache.path + File.separator + "microsoft_" + timestamp.getTime() + "_" + timestamp.getTime());
+        System.out.println("Pfad: " + Cache.PATH);
+		File file = new File(Cache.PATH + "microsoft_" + timestamp.getTime() + "_" + timestamp.getTime() + ".tmp");
 
-		System.out.println("fileCreated path: " + file);
+		System.out.println("fileCreated path: " + file.getAbsolutePath());
+		System.out.println(new File(Cache.PATH).getAbsolutePath());
 		assertTrue(file.exists());
-
-		Cache.clear();
 	}
 
 
 	@Test
-	public void findAllKeywordFilePaths(){
+	public void findAllKeywordFilePaths() throws IOException{
 		String keyword = "microsoft";
 
-		Cache.clear();
-
+			
 		Date timestamp = new Date();
 		TwitterStatusList tweetlist = new TwitterStatusList(keyword);
 		tweetlist.add(new TwitterStatus(timestamp, "inkrement", "some #fancy tweet @twitter"));
-
+		tweetlist.setDates(timestamp, timestamp);
+		
 		Cache.store(tweetlist);
 
 		File[] files = Cache.getFilePaths(keyword);
 		
-		assertEquals(files.length, 1);
+		assertEquals(1, files.length);
 		//System.out.println("files found: " + files[0].toString());
 		//System.out.println( "should be: " + Cache.path + "/" + keyword + "_" + timestamp.getTime() + "_" + timestamp.getTime() );
[…]

### 2014-11-12 src/main/java/com/aic/classification/Classifier.java
prepare the classification component

@@ -1,0 +1,14 @@
+package com.aic.classification;
+
+import edu.stanford.nlp.ling.TaggedWord;
+
+import java.util.List;
+
+public class Classifier implements IClassifier {
+
+	@Override
+	public Sentiment classify(List<? extends TaggedWord> input) {
+		// TODO implement
+		return null;
+	}
+}

### 2014-11-12 src/main/java/com/aic/classification/IClassifier.java

@@ -1,0 +1,19 @@
+package com.aic.classification;
+
+import edu.stanford.nlp.ling.TaggedWord;
+
+import java.util.List;
+
+/**
+ * Classifier for performing sentiment analysis.
+ */
+public interface IClassifier {
+
+	/**
+	 * Assigns a sentiment to the given input.
+	 *
+	 * @param input the input to classify
+	 * @return the assigned sentiment
+	 */
+	public Sentiment classify(List<? extends TaggedWord> input);
+}

### 2014-11-12 src/main/java/com/aic/classification/Sentiment.java

@@ -1,0 +1,9 @@
+package com.aic.classification;
+
+/**
+ * The possible results of sentiment classification.
+ */
+public enum Sentiment {
+	POSITIVE,
+	NEGATIVE
+}

### 2014-11-12 paper/chapters/1_introduction.tex
add introduction

@@
 
-try to cite someone \autocite{Kouloumpis2011}
+Within the last years Twitter and similar social media platforms grew considerably in terms of user numbers and mainstream fame.
+Twitter has about 284 Mio.
+active users, generating approximately 500 Mio.
+posts\footnote{posts are also known as tweets} on a single day\footnote{\url{https://about.twitter.com/company}, Effective 12.11.2014}.
+These impressive numbers show the amout of information generated by the crowd.
+Furthermore Twitter is able to reach a vast number of potential customers especially for consumer businesses.
+As a result the named services gain more and more acceptance as opinion platforms and powerful tools for both, opinion leader as well as pollister.
+This trend influenced various marketing and sales strategies and created a new market for companies specialiced on sentiment analysis of tweets, like tweetfeel\footnote{\url{www.tweetfeel.com}}, Social Mention\footnote{\url{www.socialmention.com}} and Twitratr\footnote{\url{www.twitratr.com}}.
+
+% whats sentiment analysiss
+The aim of sentiment analysis is to determine and try to measure positive and negative feelings, emotions and opinions written in a text.
+English as language allows to express the same intent in different ways.
+The main challenge therefore consists in abstracting the intention of the writer from the grammatic and language specific rules.
+
+% steps
+In general sentiment analysis can be splitted into 2 steps: a preprocessing and a constitutive sentiment analysis phase.
+In Twitter sentiment analysis there is another step right bevor preprocessing: fetching the data from the application programming interface (API).
+This task is not trivial, because the official API is limited regarding the datasets fetched within certain intervals.
+This leads to the requirement of a caching mechanism to avoid fetching the same tweets multiple times and allow the usage of more datasets.
+
+\begin{tikzpicture}[auto, node distance=3.3cm,>=latex']
+    \node [block] (input) {Twitter};
+    \node [block, right of=input, pin={[pinstyle]above:Cache}] (proprocess) {Preprocessing};
+    \node [block, right of=proprocess] (analyse) {Analysis};
+
+    \draw [->] (proprocess) -- node[name=u] {$u$} (analyse);
+    \draw [->] (input) -- node {$fetch$} (proprocess);
+\end{tikzpicture}
+
+% a lot research on how sentiment is sentiment is expressed in other media types social quite new
+While sentiment analysis of conventinal ressources like news papers or articles is quite well investigated the special research area of sentiment analysis in terms of social network posts is relatively new.
+Excpecially the possibility of priorizing keywords\footnote{known as hashtags} and the common usage of emoticons lead to advanced possibilities to categorize feelings of posts.
+
+% perfekt für marktforschung und meinungsbildung

### 2014-11-12 paper/paper.tex
Paper: Started chapter Preprocessing
add introduction

@@
-\documentclass{sig-alternate}
+\documentclass{acm_proc_article-sp}
 
@@
 
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows}
+
 \begin{document}
+\tikzstyle{block} = [draw, fill=blue!20, rectangle, 
+    minimum height=3em, minimum width=6em]
+\tikzstyle{sum} = [draw, fill=blue!20, circle, node distance=1cm]
+\tikzstyle{input} = [coordinate]
+\tikzstyle{output} = [coordinate]
+\tikzstyle{pinstyle} = [pin edge={to-,thin,black}]
 
@@
 \begin{abstract}
-
+The extensive growth of user-generated content in social networks and the common usage of emoticons and hashtags has introduced new possibilities to classify these information.
+In this paper, we provide an overview of the state-of-the-art regarding sentiment analysis of Twitter messages.
+The usefulness of existing lexical ressources and special expressions like smileys or hashtags is evaluated and an general introduction to sentiment analysis is provided as part of the introduction.
 \end{abstract}
@@
 % A category with the (minimum) three required fields
-\category{H.4}{Information Systems Applications}{Miscellaneous}
+%\category{H.4}{Information Systems Applications}{Miscellaneous}
 %A category including the fourth, optional field follows...
-\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
+%\category{D.2.8}{Software Engineering}{Metrics}[complexity measures, performance measures]
 
-\terms{Theory}
+%\terms{Theory}
 
-\keywords{ACM proceedings, \LaTeX, text tagging}
+%\keywords{ACM proceedings, \LaTeX, text tagging}
 
 \input{chapters/1_introduction.tex}
+\input{chapters/4_preprocessing.tex}
 \input{chapters/2_methods.tex}

### 2014-11-12 src/main/java/com/aic/classification/Classifier.java
update docs

@@ -7,7 +7,7 @@ import java.util.List;
 public class Classifier implements IClassifier {
 
 	@Override
-	public Sentiment classify(List<? extends TaggedWord> input) {
+	public Sentiment classify(List<? extends TaggedWord> featureVector) {
 		// TODO implement
 		return null;
 	}

### 2014-11-12 src/main/java/com/aic/classification/IClassifier.java

@@ -10,10 +10,11 @@ import java.util.List;
 public interface IClassifier {
 
 	/**
-	 * Assigns a sentiment to the given input.
+	 * Assign a sentiment to the piece of text represented by the given feature
+	 * vector.
 	 *
-	 * @param input the input to classify
+	 * @param featureVector the feature vector used for classification
 	 * @return the assigned sentiment
 	 */
-	public Sentiment classify(List<? extends TaggedWord> input);
+	public Sentiment classify(List<? extends TaggedWord> featureVector);
 }

### 2014-11-12 paper/chapters/1_introduction.tex
related work added

@@
 % a lot research on how sentiment is sentiment is expressed in other media types social quite new
-While sentiment analysis of conventinal ressources like news papers or articles is quite well investigated the special research area of sentiment analysis in terms of social network posts is relatively new.
+While sentiment analysis of conventinal ressources like news papers or articles is quite well investigated the special research area of sentiment analysis in terms of social network posts is relatively unexplored.
 Excpecially the possibility of priorizing keywords\footnote{known as hashtags} and the common usage of emoticons lead to advanced possibilities to categorize feelings of posts.
 
-% perfekt für marktforschung und meinungsbildung
+\section{Related Work}
+Sentiment analysis a growing and well explored part of Natural Langugage Processing (NLP).
+There are several papers from \citeauthor{Pang2008} regarding sentiment analysis in general and related topics like the effects of various machine learning approaches\autocite{Pang2002}\autocite{Pang2008}.
+Especially the last topic is a well studied field \autocite{Manning2000}.
+Some related research areas are document level classification, sentence-level classification and machine learning.
+Due the limited number of characters within a single twitter post, this topic is quite similar to sentance-level sentiment analysis.
+There are several recent papers regarding sentiment analysis in the context of twitter posts.
+\citeauthor{Agarwal2011} published within \citetitle{Agarwal2011} general information and techniques which cover this area\autocite{Agarwal2011}.
+In \citetitle{Kouloumpis2011} the utility of linguistic features for detecting the sentiment of tweets are investigated.
+\citeauthor{Saif2012} introduce a novel approach of adding semantics as additional features into the training set.
+For each extracted entity (e.g.
+Galaxy S) from Twitter Messages, they add a semantic concept (e.g.
+Samsung product) as an additional feature, and measure the correlation of the representative concept with negative/positive sentiment\autocite{Saif2012}.
+In \citetitle{Go2009} a algorithm is presented, which accurately classifies tweets as positive or negative, in respect to a query term\autocite{Go2009}.

### 2014-11-12 paper/paper.tex
related work added

@@
 The extensive growth of user-generated content in social networks and the common usage of emoticons and hashtags has introduced new possibilities to classify these information.
-In this paper, we provide an overview of the state-of-the-art regarding sentiment analysis of Twitter messages.
-The usefulness of existing lexical ressources and special expressions like smileys or hashtags is evaluated and an general introduction to sentiment analysis is provided as part of the introduction.
+In this paper, an overview of the state-of-the-art regarding sentiment analysis of Twitter messages is provided.
+The usefulness of existing lexical ressources and special expressions like smileys or hashtags is evaluated and an general introduction to sentiment analysis is given as part of the introduction.
 \end{abstract}

### 2014-11-27 src/main/java/com/aic/sentiment_analysis/feature/Feature.java
twitter nlp as tokenizer

@@ -19,4 +19,9 @@ public class Feature {
     public void setTag(String tag) {
         this.tag = tag;
     }
+
+    @Override
+    public String toString(){
+        return word.toString() + "_"  + tag.toString();
+    }
 }

### 2014-11-27 src/main/java/com/aic/sentiment_analysis/feature/FeatureVector.java

@@ -15,4 +15,9 @@ public class FeatureVector {
     public List<Feature> getFeatures() {
         return features;
     }
+
+    @Override
+    public String toString(){
+        return features.toString();
+    }
 }

### 2014-11-27 src/main/java/com/aic/sentiment_analysis/preprocessing/TokenType.java

@@ -1,5 +1,0 @@
-package com.aic.sentiment_analysis.preprocessing;
-
-public enum TokenType {
-   TAG, MENTIONING, WORD, SMILEY
-}

### 2014-11-27 src/main/java/com/aic/sentiment_analysis/preprocessing/TwokenizeMaxentPreprocessor.java

@@ -1,6 +1,6 @@
 package com.aic.sentiment_analysis.preprocessing;
 
-import com.aic.rest.Sentiment;
+import cmu.arktweetnlp.Twokenize;
 import com.aic.sentiment_analysis.feature.Feature;
 import com.aic.sentiment_analysis.feature.FeatureVector;
 import edu.stanford.nlp.ling.CoreLabel;
@@ -16,34 +16,44 @@ import java.util.regex.Matcher;
 import java.util.regex.Pattern;
 
 /**
- * Implementation of {@link com.aic.sentiment_analysis.preprocessing.ISentimentPreprocessor} based
+ * Implementation of {@link ISentimentPreprocessor} based
  * on the Stanford NLP framework.
  *
  * @see <a href="http://nlp.stanford.edu/software/index.shtml">Stanford NLP</a>
  * @see <a href="https://gate.ac.uk/wiki/twitter-postagger.html">POS Tagger Model file</a>
  */
 @Component
-public class SentimentTwitterPreprocessor implements ISentimentPreprocessor {
-    static final Logger logger = Logger.getLogger(SentimentTwitterPreprocessor.class.getName());
+public class TwokenizeMaxentPreprocessor implements ISentimentPreprocessor {
+    static final Logger logger = Logger.getLogger(TwokenizeMaxentPreprocessor.class.getName());
 
     private static final String URL_PATTERN = "((https?|ftp|gopher|telnet|file|Unsure|http):" +
             "((//)|(\\\\))+[\\w\\d:#@%/;$()~_?\\+-=\\\\\\.&]*)";
     private static final String HASHTAG_PATTERN = "#";
     private static final String TAGGER_PATH = "gate-EN-twitter-fast.model";
 
-    private PTBTokenizer.PTBTokenizerFactory<CoreLabel> tokenizer;
+    //private PTBTokenizer.PTBTokenizerFactory<CoreLabel> tokenizer;
     private MaxentTagger tagger;
 
-    public SentimentTwitterPreprocessor() {
+    public TwokenizeMaxentPreprocessor() {
         tagger = new MaxentTagger(TAGGER_PATH);
-        tokenizer = PTBTokenizer.PTBTokenizerFactory.newPTBTokenizerFactory(false, false);
+        //tokenizer = PTBTokenizer.PTBTokenizerFactory.newPTBTokenizerFactory(false, false);
     }
 
     @Override
     public FeatureVector preprocess(String message) throws PreprocessingException {
 
         List<Feature> features = new ArrayList<>();
[…]

### 2014-11-27 src/main/java/com/aic/ApplicationConfig.java
fixed multiple qualified beans for preprocessor

@@ -2,7 +2,9 @@ package com.aic;
 
 import com.aic.sentiment_analysis.classification.CSVTrainingSampleLoader;
 import com.aic.sentiment_analysis.classification.TrainingSample;
+import com.aic.sentiment_analysis.preprocessing.ISentimentPreprocessor;
 import com.aic.sentiment_analysis.preprocessing.PreprocessingException;
+import com.aic.sentiment_analysis.preprocessing.SentimentTwitterPreprocessor;
 import org.springframework.cache.CacheManager;
 import org.springframework.cache.annotation.EnableCaching;
 import org.springframework.cache.concurrent.ConcurrentMapCacheManager;
@@ -50,6 +52,11 @@ public class ApplicationConfig {
 			throw new IOException("Credentials incomplete!");
 		}
 	}
+
+    @Bean
+    public ISentimentPreprocessor sentimentPreprocessor(){
+        return new SentimentTwitterPreprocessor();
+    }
 
 	@Bean
 	public CacheManager cacheManager() {

### 2014-11-27 src/main/java/com/aic/sentiment_analysis/preprocessing/SentimentTwitterPreprocessor.java

@@ -22,7 +22,6 @@ import java.util.regex.Pattern;
  * @see <a href="http://nlp.stanford.edu/software/index.shtml">Stanford NLP</a>
  * @see <a href="https://gate.ac.uk/wiki/twitter-postagger.html">POS Tagger Model file</a>
  */
-@Component
 public class SentimentTwitterPreprocessor implements ISentimentPreprocessor {
     static final Logger logger = Logger.getLogger(SentimentTwitterPreprocessor.class.getName());
 

### 2014-11-27 src/main/java/com/aic/sentiment_analysis/preprocessing/TwokenizeMaxentPreprocessor.java

@@ -22,7 +22,6 @@ import java.util.regex.Pattern;
  * @see <a href="http://nlp.stanford.edu/software/index.shtml">Stanford NLP</a>
  * @see <a href="https://gate.ac.uk/wiki/twitter-postagger.html">POS Tagger Model file</a>
  */
-@Component
 public class TwokenizeMaxentPreprocessor implements ISentimentPreprocessor {
     static final Logger logger = Logger.getLogger(TwokenizeMaxentPreprocessor.class.getName());
 

### 2014-11-27 paper/chapters/2_data.tex
add twitter data section to paper

\section{Data}
Twitter is a social network and a microblogging service that
allows their users to compose and read so called 
\emph{tweets}. Each tweet 
is a text message and can contain up to 140 characters
including links, pictures\footnote{pictures are replaced 
by a url targeting a public available image resource}, and special tagged words.
These special words start with a well defined prefix 
and add semantic information to the prefixed word.
Table \ref{tab:twitterprefixes} shows an overview of 
common prefixes supported by twitter and their purpose. 
The hashtag \# tags a special word, also known as hashtag. 
It is used to mark important keywords within the tweet.
There is also a at-sign-prefix \emph{@}, which allows 
to mention other twitter users in a post. It's also possible to 
insert urls as part of the message. Regarding the hard message 
length limitation of a tweet, url-shortener are often used to
 insert longer urls.

\begin{table}[H]
\centering
\begin{tabular}{ l | c | r }                 
  prefix & name of character & meaning  \\
  \hline
  \# &  hashtag & keyword, index \\
  @ & at-sign & twitter username \\
  \hline
\end{tabular}
\caption{Common Twitter word prefixes}
\label{tab:twitterprefixes}
\end{table}

### 2014-11-27 paper/chapters/3_preprocessing.tex
add twitter data section to paper

\section{Preprocessing}
The Data-Preprocessing-Process is an essential part of sentiment-Analysis. Its goal is to prepare data
for the sentiment analysis and remove unnecessary parts.\autocite{Hemalatha2012}

Unnecessary Parts are:\autocite{Hemalatha2012}
\begin{enumerate}
    \item Remove URLs, Special Characters
    \item Filter Unnecesarry Words
    \item Remove Retweets
\end{enumerate}

Besondere an twitter: Hashtags, Mentions, Smileys
Tokenizen

### 2014-11-27 paper/chapters/2_data.tex
fix author name and twitter

@@
 Table \ref{tab:twitterprefixes} shows an overview of 
-common prefixes supported by twitter and their purpose. 
+common prefixes supported by Twitter and their purpose. 
 The hashtag \# tags a special word, also known as hashtag. 
@@
 There is also a at-sign-prefix \emph{@}, which allows 
-to mention other twitter users in a post. It's also possible to 
+to mention other Twitter users in a post. It's also possible to 
 insert urls as part of the message. Regarding the hard message 

### 2014-11-27 paper/chapters/3_preprocessing.tex
add tokenizer and preprocessing to paper

@@
 \section{Preprocessing}
-The Data-Preprocessing-Process is an essential part of sentiment-Analysis. Its goal is to prepare data
-for the sentiment analysis and remove unnecessary parts.\autocite{Hemalatha2012}
+The data preprocessing step is an essential 
+part of sentiment analysis. Its goal is to prepare data
+for the sentiment analysis and remove noisy, unnecessary, 
+inconsistent or incomplete parts.\autocite{Hemalatha2012}
+\autocite{hemalatha2012preprocessing} In a first step a
+tokenizer splits the tweet into conjugate parts, called words. 
+The resulting list of words is filtered regarding the word class, 
+the word itself and the intention of the sentiment analysis. 
+In case of sentiment analysis of twitter posts it is common to 
+remove the parts described in the following paragraphs.
+\autocite{Hemalatha2012}
 
-Unnecessary Parts are:\autocite{Hemalatha2012}
-\begin{enumerate}
-    \item Remove URLs, Special Characters
-    \item Filter Unnecesarry Words
-    \item Remove Retweets
-\end{enumerate}
+\paragraph{URLs}
+Uniform Resource Locators (URLs) refer to another site, which 
+in fact can contain very important information, but the url 
+itself is not of interest, because in the most cases it 
+contains autogenerated information, which can not be influenced 
+by the poster.
 
-Besondere an twitter: Hashtags, Mentions, Smileys
-Tokenizen
+\paragraph{Unnecesarry words}
+It is not a ovious task to classify if a word is unnecesarry 
+or not. But some word classes, like pronouns, articles orinterrogatives
+do not contain any relevant information and can be skipped. (TODO:Referenz)
+
+\paragraph{Retweets}
+Retweets reflect the postion of another person and are not always
+created to express the same position (it can also be a statement of sarcasm).
+
+\paragraph{Repeated characters}
+Everybody can post on Twitter, it is not limited 
+to professional writers, authors or similar expert groups.
+Therefore the tweets contain often deformed words 
+containing repeated characters like `heeeey' or
+`whuhuuu'. In this cases it is intended to reconstruct 
+the correct english term and only if it is not 
+possible or to sophisticated, the word is removed 
+by the preprocessor.
+
+\subsection{Tokenizer}
+There are already free tokenizer implementations
+ available. Some popular programming 
+libraries for the english language include the Stanford 
+NLP PTBTokenizer\footnote{http://nlp.stanford.edu/software/tokenizer.shtml} 
+and the Apache OpenNLP Tokenizer\footnote{http://opennlp.apache.org/documentation/manual/opennlp.html}.
+These examples are quite versatile and can be even 
+used for different tasks and languages. Another 
+example is the specialized Carnegie Mellon Twokenizer\footnote{http://www.ark.cs.cmu.edu/TweetNLP/},
+which is especially for the tokenization of tweets.
+
+It is a sophisticated task to recognize smileys. Some tokenizers.
+
+%Besondere an twitter: Hashtags, Mentions, Smileys
+Some words are difficult to handle. One example are emoticons,
+because they are hard to recognize correctly. Although they 
+are a good and popular ressource for sentiment analysis.
+
+\subsection{Tagger}

### 2014-11-28 paper/chapters/3_preprocessing.tex
backup

@@
 \subsection{Tokenizer}
-There are already free tokenizer implementations
- available. Some popular programming 
-libraries for the english language include the Stanford 
-NLP PTBTokenizer\footnote{http://nlp.stanford.edu/software/tokenizer.shtml} 
+There are already several open source tokenizer implementations
+available. Some popular programming libraries for the english 
+language include the Stanford NLP PTBTokenizer
+\footnote{http://nlp.stanford.edu/software/tokenizer.shtml} 
 and the Apache OpenNLP Tokenizer\footnote{http://opennlp.apache.org/documentation/manual/opennlp.html}.
 These examples are quite versatile and can be even 
-used for different tasks and languages. Another 
-example is the specialized Carnegie Mellon Twokenizer\footnote{http://www.ark.cs.cmu.edu/TweetNLP/},
-which is especially for the tokenization of tweets.
+used for different tasks and languages.
+The restirction of 140 Characters leads to a heavy
+usage of slang, emoticons and punctuation 
+that are uncommon in longer text messages.\autocite{davies2011}
+This circumstances give rise to specialized Tokenizer
+for tweets. One example is the specialized Carnegie 
+Mellon Twokenizer\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}.
 
@@
 because they are hard to recognize correctly. Although they 
-are a good and popular ressource for sentiment analysis.
+are a good and popular ressource for sentiment analysis. \autocite{emoticons}
 

### 2014-11-29 paper/chapters/2_data.tex
paper: update preprocessing

@@
 allows their users to compose and read so called 
-\emph{tweets}. Each tweet 
-is a text message and can contain up to 140 characters
+\emph{tweets}. The user registration it is not limited 
+to professional writers, authors or similar expert groups 
+and there are no quality safeguards or writing guidelines.
+
+Each tweet is a text message and can contain up to 140 characters
 including links, pictures\footnote{pictures are replaced 
 by a url targeting a public available image resource}, and special tagged words.
-These special words start with a well defined prefix 
-and add semantic information to the prefixed word.
+These special tagged words start with a well defined prefix 
+and add semantic information to the prefixed string.
 Table \ref{tab:twitterprefixes} shows an overview of 
 common prefixes supported by Twitter and their purpose. 
-The hashtag \# tags a special word, also known as hashtag. 
-It is used to mark important keywords within the tweet.
+The hashtag \# labels a word, also known as hashtag. 
+It is used to mark important keywords within tweets.
 There is also a at-sign-prefix \emph{@}, which allows 
-to mention other Twitter users in a post. It's also possible to 
-insert urls as part of the message. Regarding the hard message 
+to mention and link other Twitter users in a post. Tweet composers can 
+insert URLs as part of their messages. Regarding the hard 
 length limitation of a tweet, url-shortener are often used to
- insert longer urls.
+insert longer internet addresses.
 
@@
 \end{table}
+
+The combination of the 140 character restriction and
+the missing writing guidelines leads to another problem: 
+Slang, emoticons and punctuation that are uncommon in longer 
+text messages are heavily used.\autocite{davies2011}
+In terms of sentiment analysis, tweet processing is more comparable to
+sentence level analysis as paragraph analysis.
+
+%These circumstances make it even harder to  ...

### 2014-11-29 paper/chapters/3_preprocessing.tex
paper: update preprocessing

--- 2014-11-27 paper/chapters/3_preprocessing.tex
@@
 \section{Preprocessing}
-The Data-Preprocessing-Process is an essential part of sentiment-Analysis. Its goal is to prepare data
-for the sentiment analysis and remove unnecessary parts.\autocite{Hemalatha2012}
+The data preprocessing step is an essential 
+part of sentiment analysis. Its goal is to prepare data
+for the sentiment analysis and remove noisy, unnecessary, 
+inconsistent or incomplete parts.\autocite{Hemalatha2012}
+In a first step a tokenizer splits the tweet into conjugate parts, called words. 
+The resulting list of words is filtered regarding the word class, 
+the word itself and the intention of the sentiment analysis. 
+In case of sentiment analysis of twitter posts it is common to 
+remove the parts described in the following paragraphs.\autocite{Hemalatha2012}
 
-Unnecessary Parts are:\autocite{Hemalatha2012}
-\begin{enumerate}
-    \item Remove URLs, Special Characters
-    \item Filter Unnecesarry Words
-    \item Remove Retweets
-\end{enumerate}
+\paragraph{URLs}
+Uniform Resource Locators (URLs) refer to another site, which 
+in fact can contain very important information, but the internet adress 
+on its own is not of interest, because in the most cases it 
+contains only auto-generated information, which can not be influenced 
+by the poster.
 
-Besondere an twitter: Hashtags, Mentions, Smileys
-Tokenizen
+\paragraph{Unnecesarry words}
+It is not a ovious task to classify if a word is unnecesarry 
+or not. But some word classes, like pronouns, articles or interrogatives
+do not contain any relevant information and can be skipped. (TODO:Referenz)
+
+\paragraph{Retweets}
+Retweets reflect the postion of another person and are not always
+created to express the same position (e.g. statement of sarcasm).
+
+\paragraph{Repeated characters}
+Tweets contain often deformed words 
+containing repeated characters like `heeeey' or
+`whuhuuu'. In this cases it is intended to reconstruct 
+the correct english term and only if it is not 
+possible or to sophisticated, the word is removed 
+by the preprocessor.
+
+\subsection{Tokenizer}
+There are already several open source tokenizer implementations
+available. Some popular programming libraries for the english 
+language include the Stanford NLP PTBTokenizer
+\footnote{http://nlp.stanford.edu/software/tokenizer.shtml} 
+and the Apache OpenNLP Tokenizer\footnote{http://opennlp.apache.org/documentation/manual/opennlp.html}.
+These examples are quite versatile and can be even 
+used for different tasks and languages.
+To overcome the special needs of sentiment analysis in terms of Twitter posts,
+highly specialized Tokenizer were created (e.g. Carnegie 
+Mellon Twokenizer\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}).
+Some tokens like emoticons are difficult to handle. Although they 
+are a good and popular ressource for sentiment analysis. \autocite{emoticons}
+It is a sophisticated task to recognize them correctly and some Tokenizers 
+like the Stanford NLP PTBTokenizer even skips them per default. 
+The Carnegie Mellon's Twokenizer recognizes the related parts and
+forwords them to the Tagger.
+
+\subsection{Tagger}

### 2014-11-29 src/main/java/com/aic/ApplicationConfig.java
Organize imports, refactor aggregation of sentiment analyzer, add tweet classification to view

@@ -60,6 +60,6 @@ public class ApplicationConfig {
 
 	@Bean
 	public CacheManager cacheManager() {
-		return new ConcurrentMapCacheManager("sentiments");
+		return new ConcurrentMapCacheManager("sentiments", "aggregateSentiment");
 	}
 }

### 2014-11-29 src/main/java/com/aic/rest/domain/AggregateSentiment.java

@@ -1,0 +1,29 @@
+package com.aic.rest.domain;
+
+import com.aic.sentiment_analysis.classification.Sentiment;
+import com.aic.sentiment_analysis.fetch.TwitterStatus;
+
+import java.util.Map;
+
+public class AggregateSentiment {
+    private Map<TwitterStatus, Sentiment> sentiments;
+    private double sentimentRatio;
+
+    public AggregateSentiment(com.aic.sentiment_analysis.AggregateSentiment aggregateSentiment) {
+        this.sentiments = aggregateSentiment.getSentimentAggregation();
+        this.sentimentRatio = aggregateSentiment.calculateAggregateSentimentRatio();
+    }
+
+    /**
+     * Returns a map of tweets with the corresponding sentiment.
+     *
+     * @return a map of tweets with the corresponding sentiment
+     */
+    public Map<TwitterStatus, Sentiment> getSentimentAggregation() {
+        return sentiments;
+    }
+
+    public double getSentimentRatio() {
+        return sentimentRatio;
+    }
+}

### 2014-11-29 src/main/java/com/aic/sentiment_analysis/SentimentAnalyzer.java

@@ -40,6 +40,51 @@ public class SentimentAnalyzer {
 		this.preprocessor = preprocessor;
 	}
 
+    /**
+     * Calculates a sentiment value based on an aggregation of tweets and
+     * each tweet classified by a sentiment
+     * {@link com.aic.sentiment_analysis.classification.Sentiment} value based
+     * on the tweets that have been posted during a specific observation period.
+     *
+     * @param companyName the according company's name
+     * @param start the start of the observation period
+     * @param end the end of the observation period
+     * @return an aggregated sentiment
+     * @throws SentimentAnalysisException
+     */
+    @Cacheable("aggregateSentiment")
+    public AggregateSentiment aggregateSentiment(String companyName, Date start, Date end)
+            throws SentimentAnalysisException {
+        AggregateSentiment aggregateSentiment = new AggregateSentiment();
+        try {
+            List<TwitterStatus> tweets = tweetLoader.load(companyName, start, end);
+
+            if (tweets.size() == 0) {
+                throw new SentimentAnalysisException("No tweets available for analysis.");
+            }
+
+            for (TwitterStatus tweet : tweets) {
+                FeatureVector featureVector = null;
+                featureVector = preprocessor.preprocess(tweet.getText());
+
+                Sentiment sentiment = classifier.classify(featureVector);
+
+                aggregateSentiment.putSentiment(tweet, sentiment);
+
+                logger.debug("Classified \"" + tweet.getText() +
+                        "\" as " + sentiment.name());
+            }
+
+            logger.debug(String.format("Aggregated sentiment is %.2f",
+                    aggregateSentiment.calculateAggregateSentimentRatio()));
+            return aggregateSentiment;
+        } catch (PreprocessingException e) {
+            throw new SentimentAnalysisException(e);
+        } catch (ClassificationException e) {
+            throw new SentimentAnalysisException(e);
+        }
+    }
+
 	/**
 	 * Calculate the public perception of the company with the given name, based
 	 * on the tweets that have been posted during a specific observation period.
@@ -54,6 +99,7 @@ public class SentimentAnalyzer {
 	@Cacheable("sentiments")
 	public float averageSentiment(String companyName, Date start, Date end)
 			throws SentimentAnalysisException {
+        AggregateSentiment aggregateSentiment = new AggregateSentiment();
 		try {
[…]

### 2014-11-29 src/main/java/com/aic/sentiment_analysis/feature/Feature.java

@@ -1,5 +1,9 @@
 package com.aic.sentiment_analysis.feature;
 
+/**
+ * Represents a feature which consists of
+ * a tag and a word.
+ */
 public class Feature {
 
     private String word = "";

### 2014-11-29 src/main/java/com/aic/sentiment_analysis/fetch/TwitterStatusList.java

@@ -1,7 +1,7 @@
 package com.aic.sentiment_analysis.fetch;
 
-import java.util.Date;
 import java.util.ArrayList;
+import java.util.Date;
 
 // TODO javadoc	
 public class TwitterStatusList extends ArrayList<TwitterStatus> implements Comparable<TwitterStatusList>

### 2014-11-29 src/main/java/com/aic/sentiment_analysis/preprocessing/SentimentTwitterPreprocessor.java

@@ -1,12 +1,10 @@
 package com.aic.sentiment_analysis.preprocessing;
 
-import com.aic.rest.Sentiment;
 import com.aic.sentiment_analysis.feature.Feature;
 import com.aic.sentiment_analysis.feature.FeatureVector;
 import edu.stanford.nlp.ling.CoreLabel;
 import edu.stanford.nlp.process.PTBTokenizer;
 import edu.stanford.nlp.tagger.maxent.MaxentTagger;
-import org.springframework.stereotype.Component;
 
 import java.io.StringReader;
 import java.util.ArrayList;

### 2014-11-29 src/main/java/com/aic/sentiment_analysis/preprocessing/TwokenizeMaxentPreprocessor.java

@@ -4,11 +4,8 @@ import cmu.arktweetnlp.Twokenize;
 import com.aic.sentiment_analysis.feature.Feature;
 import com.aic.sentiment_analysis.feature.FeatureVector;
 import edu.stanford.nlp.ling.CoreLabel;
-import edu.stanford.nlp.process.PTBTokenizer;
 import edu.stanford.nlp.tagger.maxent.MaxentTagger;
-import org.springframework.stereotype.Component;
 
-import java.io.StringReader;
 import java.util.ArrayList;
 import java.util.List;
 import java.util.logging.Logger;

### 2014-11-29 src/test/java/com/aic/sentiment_analysis/fetch/TwitterStatusListTest.java

@@ -1,11 +1,10 @@
 package com.aic.sentiment_analysis.fetch;
 
-import com.aic.sentiment_analysis.fetch.TwitterStatus;
-import com.aic.sentiment_analysis.fetch.TwitterStatusList;
-import org.junit.* ;
-import static org.junit.Assert.* ;
+import org.junit.Test;
 
 import java.util.Date;
+
+import static org.junit.Assert.assertEquals;
 
 public class TwitterStatusListTest{
 

### 2014-11-30 paper/chapters/3_preprocessing.tex
Some typofixes and extension of tagger subsection.

@@
 Uniform Resource Locators (URLs) refer to another site, which 
-in fact can contain very important information, but the internet adress 
-on its own is not of interest, because in the most cases it 
+in fact can contain very important information, but the internet address
+on its own is not of interest, because in most cases it
 contains only auto-generated information, which can not be influenced 
@@
 \paragraph{Unnecesarry words}
-It is not a ovious task to classify if a word is unnecesarry 
+It is not an obvious task to classify if a word is unnecessary
 or not. But some word classes, like pronouns, articles or interrogatives
@@
 \paragraph{Retweets}
-Retweets reflect the postion of another person and are not always
-created to express the same position (e.g. statement of sarcasm).
+Retweets reflect the position of another person and are not always
+created to express the same opinion (e.g. statement of sarcasm).
 
@@
 the correct english term and only if it is not 
-possible or to sophisticated, the word is removed 
+possible or too sophisticated, the word is removed
 by the preprocessor.
@@
 and the Apache OpenNLP Tokenizer\footnote{http://opennlp.apache.org/documentation/manual/opennlp.html}.
-These examples are quite versatile and can be even 
+These examples are quite versatile and can even be
 used for different tasks and languages.
@@
 Some tokens like emoticons are difficult to handle. Although they 
-are a good and popular ressource for sentiment analysis. \autocite{emoticons}
+are a good and popular resource for sentiment analysis. \autocite{emoticons}
 It is a sophisticated task to recognize them correctly and some Tokenizers 
@@
 The Carnegie Mellon's Twokenizer recognizes the related parts and
-forwords them to the Tagger.
+forwards them to the Tagger.
 
 \subsection{Tagger}
+Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefor
+very useful for Natural Language Processing.
+Tagging Tweets is very challenging, because of the twitter specific slang, emoticons and the lack of conventional orthography.
+%TODO: Quelle: Part-of-Speech Tagging for Twitter: Annotation, Features, and Experiments
+There is a variety of freely downloadable POS taggers
+\footnote{http://www-nlp.stanford.edu/links/statnlp.html} e.g. Stanford POS tagger
+\footnote{http://nlp.stanford.edu/software/tagger.shtml}
+ but just a few are specialized on tagging twitter data like the TweetNLP tagger
+\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}. In comparison with the Stanford POS tagger the TweetNLP tagger
+ reduces errors by 25\%.
+ %TODO Quelle: http://iswc2012.semanticweb.org/sites/default/files/76490497.pdf

### 2014-12-04 paper/chapters/2_data.tex

@@
 \section{Data}
-Twitter is a social network and a microblogging service that
+Twitter is a social network and microblogging service that
 allows their users to compose and read so called 
-\emph{tweets}. The user registration it is not limited 
+\emph{tweets}. The user registration is not limited
 to professional writers, authors or similar expert groups 
@@
 common prefixes supported by Twitter and their purpose. 
-The hashtag \# labels a word, also known as hashtag. 
+A hash (\#) labels a word, also known as hashtag.
 It is used to mark important keywords within tweets.

### 2014-12-04 src/main/java/com/aic/sentiment_analysis/AggregateSentiment.java
weight sentiment with date

@@ -3,8 +3,7 @@ package com.aic.sentiment_analysis;
 import com.aic.sentiment_analysis.classification.Sentiment;
 import com.aic.sentiment_analysis.fetch.TwitterStatus;
 
-import java.util.HashMap;
-import java.util.Map;
+import java.util.*;
 
 /**
  * Represents an aggregation of tweets {@link com.aic.sentiment_analysis.fetch.TwitterStatus} which
@@ -28,8 +27,10 @@ public class AggregateSentiment {
     public void putSentiment(TwitterStatus status, Sentiment sentiment) {
         sentiments.put(status, sentiment);
 
-        if (sentiment == Sentiment.POSITIVE)
+        if (sentiment == Sentiment.POSITIVE) {
             positiveTweetsCount++;
+            positiveStats.add(status);
+        }
     }
 
     /**
@@ -48,5 +49,59 @@ public class AggregateSentiment {
      */
     public float calculateAggregateSentimentRatio() {
         return (float) positiveTweetsCount / sentiments.size();
+    }
+
+
+    /**
+     * ################## Weight tweets based on Date ####################
+     * if location does not work
+     * TODO delete section if no neccessary
+     */
+
+    private ArrayList<TwitterStatus> positiveStats = new ArrayList<>();
+
+    /**
+     *
+     * @return weighted aggregated setiment ratio
+     */
+    public float calculateAggregateSentimentRatio1() {
+
+        float sent = 0;
+        //The last tweet has 90% of the weight of the first one
+        double endRatio = 0.8;
+        int size = positiveStats.size();
+
+        orderTweets();
+
+        if(size == 1){
+            return 1/sentiments.size();
+        }
+
+        for(int i = 0; i < positiveStats.size(); i++){
+            sent += 1-i*(1-endRatio)/(size-1);
+        }
+
+        //System.out.println("############### sent new: " + sent/sentiments.size());
+
+        return sent/sentiments.size();
+    }
+
+    private void orderTweets(){
+
+        Collections.sort(positiveStats, new Comparator<TwitterStatus>() {
+
+            public int compare(TwitterStatus tw1, TwitterStatus tw2) {
+                return (int) tw2.getDate().getTime() - (int) tw1.getDate().getTime();
+            }
+        });
+
+        /*
+        System.out.println("############################");
+        System.out.println(positiveStats.size());
+        for(TwitterStatus t : positiveStats){
+            System.out.println(t.getDate().getTime());
+        }
+        System.out.println("############################");
+        */
     }
 }

### 2014-12-04 src/main/java/com/aic/sentiment_analysis/SentimentAnalyzer.java

@@ -77,6 +77,8 @@ public class SentimentAnalyzer {
 
             logger.debug(String.format("Aggregated sentiment is %.2f",
                     aggregateSentiment.calculateAggregateSentimentRatio()));
+			logger.debug(String.format("Weighted Aggregated sentiment is %.2f",
+					aggregateSentiment.calculateAggregateSentimentRatio1()));
             return aggregateSentiment;
         } catch (PreprocessingException e) {
             throw new SentimentAnalysisException(e);

### 2014-12-04 src/main/java/com/aic/sentiment_analysis/AggregateSentiment.java
rename

@@ -64,7 +64,7 @@ public class AggregateSentiment {
      *
      * @return weighted aggregated setiment ratio
      */
-    public float calculateAggregateSentimentRatio1() {
+    public float calculateDateWeightedAggregateSentimentRatio() {
 
         float sent = 0;
         //The last tweet has 90% of the weight of the first one

### 2014-12-04 src/main/java/com/aic/sentiment_analysis/SentimentAnalyzer.java

@@ -78,7 +78,7 @@ public class SentimentAnalyzer {
             logger.debug(String.format("Aggregated sentiment is %.2f",
                     aggregateSentiment.calculateAggregateSentimentRatio()));
 			logger.debug(String.format("Weighted Aggregated sentiment is %.2f",
-					aggregateSentiment.calculateAggregateSentimentRatio1()));
+					aggregateSentiment.calculateDateWeightedAggregateSentimentRatio()));
             return aggregateSentiment;
         } catch (PreprocessingException e) {
             throw new SentimentAnalysisException(e);

### 2014-12-04 src/main/java/com/aic/rest/domain/AggregateSentiment.java
display weighted sentiment in UI

@@ -8,10 +8,12 @@ import java.util.Map;
 public class AggregateSentiment {
     private Map<TwitterStatus, Sentiment> sentiments;
     private double sentimentRatio;
+    private double dateWeightedSentimentRatio;
 
     public AggregateSentiment(com.aic.sentiment_analysis.AggregateSentiment aggregateSentiment) {
         this.sentiments = aggregateSentiment.getSentimentAggregation();
         this.sentimentRatio = aggregateSentiment.calculateAggregateSentimentRatio();
+        this.dateWeightedSentimentRatio = aggregateSentiment.calculateDateWeightedAggregateSentimentRatio();
     }
 
     /**
@@ -25,5 +27,9 @@ public class AggregateSentiment {
 
     public double getSentimentRatio() {
         return sentimentRatio;
+    }
+
+    public double getDateWeightedSentimentRatio() {
+        return dateWeightedSentimentRatio;
     }
 }

### 2014-12-04 src/main/java/com/aic/sentiment_analysis/AggregateSentiment.java
corrected date weight mechanism

@@ -14,6 +14,8 @@ public class AggregateSentiment {
     private Map<TwitterStatus, Sentiment> sentiments;
     private int positiveTweetsCount;
 
+    private ArrayList<TwitterStatus> stats;
+
     public AggregateSentiment() {
         this.sentiments = new HashMap<>();
     }
@@ -29,7 +31,6 @@ public class AggregateSentiment {
 
         if (sentiment == Sentiment.POSITIVE) {
             positiveTweetsCount++;
-            positiveStats.add(status);
         }
     }
 
@@ -53,55 +54,45 @@ public class AggregateSentiment {
 
 
     /**
-     * ################## Weight tweets based on Date ####################
-     * if location does not work
-     * TODO delete section if no neccessary
-     */
-
-    private ArrayList<TwitterStatus> positiveStats = new ArrayList<>();
-
-    /**
-     *
-     * @return weighted aggregated setiment ratio
+     * Calculate the sentiment weighted by date
+     * @return weighted sentiment value
      */
     public float calculateDateWeightedAggregateSentimentRatio() {
 
-        float sent = 0;
-        //The last tweet has 90% of the weight of the first one
-        double endRatio = 0.8;
-        int size = positiveStats.size();
+        stats = new ArrayList<>(sentiments.keySet());
 
-        orderTweets();
+        float overallWeight = 0;
+        float singleWeight = 0;
+        float decreaseFactor = 0.2f;
+        int statsSize = stats.size();
 
-        if(size == 1){
-            return 1/sentiments.size();
+        orderTweetsByDate();
+
+        TwitterStatus ts;
+
+        for(int i = 0; i < statsSize; i++){
+            ts = stats.get(i);
+            if(sentiments.get(ts) == Sentiment.POSITIVE){
+                singleWeight += 1-i*decreaseFactor/(statsSize-1);
+                overallWeight += 1-i*decreaseFactor/(statsSize-1);
+            }else{
+                overallWeight++;
+            }
         }
 
-        for(int i = 0; i < positiveStats.size(); i++){
-            sent += 1-i*(1-endRatio)/(size-1);
-        }
-
-        //System.out.println("############### sent new: " + sent/sentiments.size());
-
-        return sent/sentiments.size();
+        return singleWeight/overallWeight;
     }
 
-    private void orderTweets(){
+    /**
+     * Order tweets by date
+     */
+    private void orderTweetsByDate(){
 
-        Collections.sort(positiveStats, new Comparator<TwitterStatus>() {
[…]

### 2014-12-05 src/main/java/com/aic/sentiment_analysis/preprocessing/SentimentTwitterPreprocessor.java
Remove logging in preprocessing

@@ -42,8 +42,6 @@ public class SentimentTwitterPreprocessor implements ISentimentPreprocessor {
         List<Feature> features = new ArrayList<>();
         List<CoreLabel> coreLabels = tokenizer.getTokenizer(new StringReader(message)).tokenize();
 
-        logger.info(coreLabels.toString());
-
         // tag labels
         tagger.tagCoreLabels(coreLabels);
 

### 2014-12-05 src/test/java/com/aic/sentiment_analysis/preprocessing/TweetPreprocessTest.java

@@ -54,4 +54,17 @@ public class TweetPreprocessTest {
         Assert.assertFalse("'https://wikipedia.org' not found",  features.contains("https://wikipedia.org"));
         Assert.assertFalse("'http://www.wikipedia.org' not found",  features.contains("http://www.wikipedia.org"));
     }
+
+    /**
+     * Tests if a username is contained in the feature vector.
+     */
+    @Test
+    public void testIfUsernameContained() throws PreprocessingException {
+        FeatureVector featureVector = preprocessor.preprocess("Trying to test @codeship stuff");
+        List<String> features = new ArrayList<>();
+        for (Feature f : featureVector.getFeatures()) {
+            features.add(f.getWord());
+        }
+        Assert.assertFalse("'@codeship' found but should not be part of the message", features.contains("@codeship"));
+    }
 }

### 2014-12-05 src/main/java/com/aic/rest/controller/CompanyController.java
Remove password for registration

@@ -44,8 +44,10 @@ public class CompanyController {
     @RequestMapping(value = "/register", method = RequestMethod.POST)
     @ResponseBody
     public ResponseEntity<Company> register(@RequestBody Company company) throws RestException {
-        if (companies.containsKey(company.getName()))
-            throw new RestException("Company already exists");
+        if (companies.containsKey(company.getName())) {
+            return new ResponseEntity<>(company, HttpStatus.OK);
+            //throw new RestException("Company already exists");
+        }
 
         companies.put(company.getName(), company);
         return new ResponseEntity<>(company, HttpStatus.OK);
@@ -66,9 +68,12 @@ public class CompanyController {
             return false;
         }
         Company storedCompany = companies.get(name);
+        /*
         if (!storedCompany.getPassword().equals(password)) {
             return false;
         }
+        */
+
         return true;
     }
 
@@ -76,20 +81,20 @@ public class CompanyController {
      * Calculates the sentiment for the given company within the period.
      *
      * @param name name of the company
-     * @param password password of the company
+     * //@param password password of the company
      * @param start start date for the sentiment analysis
      * @param end end date for the sentiment analysis
      */
     @RequestMapping(value = "/sentiment", method = RequestMethod.GET)
     @ResponseBody
     public AggregateSentiment sentiment(@RequestParam(value = "name") String name,
-                           @RequestParam(value = "password") String password,
+                           //@RequestParam(value = "password") String password,
                            @RequestParam(value = "startDate")
                            @DateTimeFormat(pattern = "yyyy-MM-dd") Date start,
                            @RequestParam(value = "endDate")
                            @DateTimeFormat(pattern = "yyyy-MM-dd") Date end) throws RestException, SentimentAnalysisException {
-        if (!isAuthorized(name, password))
-            throw new RestException("Authorization failed");
+        /*if (!isAuthorized(name, password))
+            throw new RestException("Authorization failed");*/
 
         // Wrapping aggregateSentiment for Jackson
         AggregateSentiment aggregateSentiment = new AggregateSentiment(

### 2014-12-05 src/main/java/com/aic/rest/domain/Company.java

@@ -3,13 +3,13 @@ package com.aic.rest.domain;
 public class Company {
 
     private String name;
-    private String password;
+    //private String password;
 
     public Company() { }
 
     public Company(String name, String password) {
         this.name = name;
-        this.password = password;
+        //this.password = password;
     }
 
     public String getName() {
@@ -20,11 +20,12 @@ public class Company {
         this.name = name;
     }
 
+    /*
     public String getPassword() {
         return password;
     }
 
     public void setPassword(String password) {
         this.password = password;
-    }
+    }*/
 }

### 2014-12-05 src/main/resources/static/js/controller/SentimentController.js

@@ -23,14 +23,16 @@ var SentimentController = function($scope, $http, $location) {
         $http.get("sentiment", {
             params: {
                 name: sentimentCompany.name,
-                password: sentimentCompany.password,
+                //password: sentimentCompany.password,
                 startDate: range.start,
                 endDate: range.end
             }
         }).success(function(data) {
             $scope.sentiment = data;
             $scope.showSentiment = true;
-        }).error(function(){
+        }).error(function(data, status, headers, config){
+            $scope.errorTextAlert = "Could not fetch tweets: " + data.message;
+            $scope.showErrorAlert = true;
             $scope.showSentiment = false;
         });
     }

### 2014-12-05 slides/presentation-1.tex
Add slides for first presentation

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Head matter - can we try to be consistent on
% included packages
\documentclass{beamer}
\mode<presentation>
{\usetheme{default}
 \usecolortheme{default}
 \usefonttheme{default}
 \setbeamertemplate{navigation symbols}{}
 \setbeamertemplate{caption}[numbered]} 
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{graphicx}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting for title page
\title[Twitter Sentiment Analysis]{Twitter Sentiment Analysis}
\author{Christian Hotz-Behofsits, Dominik Pichler, Matthias Reisinger, Thomas Schmidleithner, Florian Taus}
\institute{Advanced Internet Computing}
\date{5th December 2014}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}
  \titlepage
\end{frame}
%\section{Introduction}
% There is actually no point to the sections 
% since we are not using table of contents mark up
\begin{frame}{Introduction}
\begin{block}{Aim}
Aggregate sentiment values of different tweets by a value specific keyword via the Twitter API.
\end{block}
\begin{itemize}
   \item Load Tweets from Twitter API
   \item Preprocessing
   \item Classification
   \item Aggregation of overall sentiment
\end{itemize}
\end{frame}

\begin{frame}{Twitter API}
Twitter offers several APIs for different purposes. All require authorization and a valid Twitter API-account.

\begin{itemize}
	\item REST API
	\begin{itemize}
    	\item limited to 180 GET-Request/Minute
        \item fetch all tweets at once
    \end{itemize}
    \item Streaming API
	\begin{itemize}
    	\item no limitation regarding tweets per minute
        \item continuous tweet-stream
    \end{itemize}
\end{itemize}
\end{frame}

% Commands to include a figure:
%\begin{figure}
%\includegraphics[width=\textwidth]{your-figure's-file-name}
%\caption{\label{fig:your-figure}Caption goes here.}
%\end{figure}

\begin{frame}{Preprocessing}
\begin{block}{}
Preprocess a tweet message and extract important information (feature vector) for classification.
\end{block}
\begin{itemize}
	\item[Tokenizer]
    splits input into related parts (tokens). e.g. Stanford NLP PTBTokenizer, Carnegie Mellon Twokenizer
	\item[Tagger]
    adds information to each token (e.g. word-class).  e.g Stanford NLP MaxentTagger
	\item[Filter token list] 
    filtering based on tagged-information. 
\end{itemize}

\end{frame}

\begin{frame}{Classification}
%\begin{block}{}
%Classification aims at dividing inputs into at least two classes by the use of a learned model.
%\end{block}
\begin{itemize}
	\item Aims at dividing inputs into at least two classes
    \item In this course: assign sentiments to textual inputs
    \item Supervised and unsupervised approaches
    \item Common supervised algorithms: Support vector machines (SVM), naive bayes, \ldots
    \begin{itemize}
        \item Textual input in form of a \emph{feature vector}
        \item The feature vector contains relevant words such as verbs, adjectives and hashtags
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Classification (Implementation)}
\begin{itemize}
	\item Based on WEKA
    \item SVM as classifier (LibSVM)
    \item Train model with stanford twitter test corpus\footnote{\tiny{http://help.sentiment140.com/for-students}} (manually reduced to 1000 positive and 1000 negative instances)
	\item Evaluation with testset (359 instances):\\ \textbf{64.35 \%} classified correctly
\end{itemize}
\end{frame}

\begin{frame}{Aggregate Classified Sentiments}
Calcuate the weighted sentiment for each tweet whereby more recent dates are weighted heavier
\begin{itemize}
	\item The weight of the most recent positive tweet is 1
    \item The weight of the oldest is 0.8
    \item The weights in between decrease linear
    \item $\sum_{i = 0}^{\#tweets-1}1-i*\frac{decreaseFactor}{\#tweets-1}$
    \item Just positive tweets are weighted
\end{itemize}
\end{frame}

\begin{frame}{Prototype}
Some libraries and attributes of our prototype.

\begin{itemize}
	\item Spring Boot
    \item REST Backend
    \item AngularJS Frontend
    \item PTBTokenizer and Twokenizer
    \item Maxent Tagger
    \item Weka
\end{itemize}

\begin{block}{}
$\rightarrow$ live demo!
\end{block}

\begin{block}{}
Code available at: https://github.com/inkrement/aic
\end{block}

\end{frame}

\end{document}

### 2015-01-20 src/main/java/com/aic/sentiment_analysis/classification/SentimentClassifier.java
add debug output

@@ -5,6 +5,8 @@ import com.aic.sentiment_analysis.feature.FeatureVector;
 import com.aic.sentiment_analysis.preprocessing.ISentimentPreprocessor;
 import com.aic.sentiment_analysis.preprocessing.PreprocessingException;
 import com.aic.sentiment_analysis.preprocessing.SentimentTwitterPreprocessor;
+import org.apache.commons.logging.Log;
+import org.apache.commons.logging.LogFactory;
 import org.springframework.beans.factory.annotation.Autowired;
 import org.springframework.stereotype.Component;
 import weka.classifiers.Classifier;
@@ -26,6 +28,8 @@ import java.util.*;
  */
 public class SentimentClassifier implements ISentimentClassifier {
 
+	private static final Log logger = LogFactory.getLog(SentimentClassifier.class);
+
 	private final Classifier classifier;
 	private final Instances trainingInstances;
 	private final ArrayList<Attribute> featureList;
@@ -42,6 +46,17 @@ public class SentimentClassifier implements ISentimentClassifier {
 		featureList = loadFeatureList(trainingSamples);
 		featureIndexMap = initFeatureIndexMap(featureList);
 		trainingInstances = loadInstances("train", trainingSamples, featureList);
+
+		// debug output
+		StringBuilder featureString = new StringBuilder();
+		for (Attribute feature : featureList) {
+			featureString.append('{');
+			featureString.append(feature);
+			featureString.append("}, ");
+		}
+		featureString.delete(featureString.length() - 2, featureString.length());
+		logger.debug("The following features are used for classification: [" + featureString + "]");
+
 		train();
 	}
 
@@ -81,6 +96,7 @@ public class SentimentClassifier implements ISentimentClassifier {
 		for (TrainingSample trainingSample : trainingSamples) {
 			FeatureVector featureVector = trainingSample.getFeatureVector();
 			for (Feature feature : featureVector.getFeatures()) {
+				logger.debug("Add feature for word '" + feature.getWord() + "'");
 				features.add(feature.getWord());
 			}
 		}
@@ -113,10 +129,15 @@ public class SentimentClassifier implements ISentimentClassifier {
 	}
 
 	private Instance loadInstance(FeatureVector featureVector, Sentiment sentiment) {
+		logger.debug("loadInstance");
+
 		TreeMap<Integer, Double> featureMap = new TreeMap<>();
[…]

### 2015-01-20 src/main/java/com/aic/ApplicationConfig.java
refine loading of training instances

@@ -25,7 +25,7 @@ import java.util.Properties;
 public class ApplicationConfig {
 
 	@Bean
-	public Iterable<TrainingSample>	trainingSamples() throws URISyntaxException,
+	public List<TrainingSample> trainingSamples() throws URISyntaxException,
 			PreprocessingException, FileNotFoundException {
 		ICSVTrainingLoader sampleLoader = new CSVTrainingSampleLoader();
 		//ICSVTrainingLoader sampleLoader = new CSVTrainingSTSLoader();

### 2015-01-20 src/main/java/com/aic/sentiment_analysis/classification/SentimentClassifier.java

@@ -2,20 +2,13 @@ package com.aic.sentiment_analysis.classification;
 
 import com.aic.sentiment_analysis.feature.Feature;
 import com.aic.sentiment_analysis.feature.FeatureVector;
-import com.aic.sentiment_analysis.preprocessing.ISentimentPreprocessor;
 import com.aic.sentiment_analysis.preprocessing.PreprocessingException;
-import com.aic.sentiment_analysis.preprocessing.SentimentTwitterPreprocessor;
 import org.apache.commons.logging.Log;
 import org.apache.commons.logging.LogFactory;
-import org.springframework.beans.factory.annotation.Autowired;
-import org.springframework.stereotype.Component;
 import weka.classifiers.Classifier;
 import weka.classifiers.Evaluation;
 import weka.classifiers.functions.LibSVM;
-import weka.core.Attribute;
-import weka.core.Instance;
-import weka.core.Instances;
-import weka.core.SparseInstance;
+import weka.core.*;
 
 import java.util.*;
 
@@ -40,12 +33,10 @@ public class SentimentClassifier implements ISentimentClassifier {
 	 * @param algorithm the concrete classification algorithm to use
 	 * @throws ClassificationException
 	 */
-	public SentimentClassifier(Iterable<TrainingSample> trainingSamples, Classifier algorithm)
+	public SentimentClassifier(List<TrainingSample> trainingSamples, Classifier algorithm)
 			throws ClassificationException {
 		classifier = new LibSVM();
 		featureList = loadFeatureList(trainingSamples);
-		featureIndexMap = initFeatureIndexMap(featureList);
-		trainingInstances = loadInstances("train", trainingSamples, featureList);
 
 		// debug output
 		StringBuilder featureString = new StringBuilder();
@@ -55,7 +46,10 @@ public class SentimentClassifier implements ISentimentClassifier {
 			featureString.append("}, ");
 		}
 		featureString.delete(featureString.length() - 2, featureString.length());
-		logger.debug("The following features are used for classification: [" + featureString + "]");
+		logger.debug("The following " + featureList.size() + " features are used for classification: [" + featureString + "]");
+
+		featureIndexMap = initFeatureIndexMap(featureList);
+		trainingInstances = loadInstances("train", trainingSamples, featureList);
 
 		train();
 	}
@@ -73,15 +67,15 @@ public class SentimentClassifier implements ISentimentClassifier {
[…]

### 2015-01-20 src/test/java/com/aic/sentiment_analysis/classification/EvaluationTest.java

@@ -1,6 +1,7 @@
 package com.aic.sentiment_analysis.classification;
 
 import com.aic.Constants;
+import com.aic.sentiment_analysis.ClassifierConfiguration;
 import com.aic.sentiment_analysis.preprocessing.PreprocessingException;
 import org.junit.BeforeClass;
 import org.junit.Test;
@@ -8,17 +9,20 @@ import weka.classifiers.Classifier;
 import weka.classifiers.Evaluation;
 import weka.classifiers.bayes.NaiveBayes;
 import weka.classifiers.functions.LibSVM;
+import weka.classifiers.lazy.IBk;
+import weka.classifiers.trees.J48;
 import weka.core.SelectedTag;
 
 import java.io.FileNotFoundException;
 import java.net.URISyntaxException;
+import java.util.List;
 
 public class EvaluationTest {
 
 	private static final String PATH_TO_TEST_DATA = "testdata.manual.2009.06.14.csv";
 
-	private static Iterable<TrainingSample> trainingSamples;
-	private static Iterable<TrainingSample> testSamples;
+	private static List<TrainingSample> trainingSamples;
+	private static List<TrainingSample> testSamples;
 
 	@BeforeClass
 	public static void loadTrainingData() throws URISyntaxException, PreprocessingException, FileNotFoundException {
@@ -33,7 +37,8 @@ public class EvaluationTest {
 	@Test
 	public void evaluateLibSVM_C_SVC() throws ClassificationException {
 		LibSVM svm = new LibSVM();
-		svm.setSVMType(new SelectedTag(LibSVM.SVMTYPE_C_SVC, LibSVM.TAGS_SVMTYPE));
+		svm.setDegree(100);
+		svm.setGamma(12345);
 		evaluate(svm);
 	}
 
@@ -70,6 +75,18 @@ public class EvaluationTest {
 		NaiveBayes naiveBayes = new NaiveBayes();
 		naiveBayes.setUseSupervisedDiscretization(true);
 		evaluate(naiveBayes);
+	}
+
+	@Test
+	public void evaluateIBk() throws ClassificationException {
+		IBk ibk = new IBk();
+		evaluate(ibk);
+	}
+
+	@Test
+	public void evaluateJ48() throws ClassificationException {
+		J48 j48 = new J48();
+		evaluate(j48);
 	}
 
 	public void evaluate(Classifier algorithm) throws ClassificationException {

### 2015-01-20 src/main/java/com/aic/sentiment_analysis/classification/CSVTrainingSTSLoader.java
Change STS_GOLD Training Set

@@ -32,13 +32,13 @@ public class CSVTrainingSTSLoader implements ICSVTrainingLoader {
 
 		while (scanner.hasNextLine()) {
 			String line = scanner.nextLine();
-			String[] columns = line.substring(0, line.length() - 1).split(";");
+			String[] columns = line.substring(0, line.length() - 1).split(",");
 
-			String sentimentString = columns[0];
+			String sentimentString = columns[1];
 			Sentiment sentiment;
-			if (sentimentString.equals("0")) {
+			if (sentimentString.equals("neg")) {
 				sentiment = Sentiment.NEGATIVE;
-			} else if (sentimentString.equals("4")) {
+			} else if (sentimentString.equals("pos")) {
 				sentiment = Sentiment.POSITIVE;
 			} else {
 				continue;

### 2015-01-20 src/main/resources/static/js/controller/SentimentController.js

@@ -5,8 +5,6 @@
  */
 var SentimentController = function($scope, $http, $location) {
 
-    $scope.classifier = {};
-
     /* Helper function for current active menu in view */
     $scope.isActive = function (viewLocation) {
         var active = (viewLocation === $location.path());

### 2015-01-20 src/main/java/com/aic/ApplicationConfig.java
Change STS_GOLD Training Set

@@ -27,8 +27,8 @@ public class ApplicationConfig {
 	@Bean
 	public List<TrainingSample> trainingSamples() throws URISyntaxException,
 			PreprocessingException, FileNotFoundException {
-		ICSVTrainingLoader sampleLoader = new CSVTrainingSampleLoader();
-		//ICSVTrainingLoader sampleLoader = new CSVTrainingSTSLoader();
+		//ICSVTrainingLoader sampleLoader = new CSVTrainingSampleLoader();
+		ICSVTrainingLoader sampleLoader = new CSVTrainingSTSLoader();
 		URI trainingSetUri = getClass().getClassLoader().
 				getResource(Constants.CLASSIFIER_TRAINING_FILE_PATH).toURI();
 		List<TrainingSample> samples = sampleLoader.load(trainingSetUri);

### 2015-01-20 src/test/java/com/aic/sentiment_analysis/classification/EvaluationTest.java
play around with evalution tests

@@ -37,8 +37,20 @@ public class EvaluationTest {
 	@Test
 	public void evaluateLibSVM_C_SVC() throws ClassificationException {
 		LibSVM svm = new LibSVM();
-		svm.setDegree(100);
-		svm.setGamma(12345);
+		svm.setCacheSize(40);
+		svm.setCoef0(0.0);
+		svm.setCost(1);
+		svm.setDegree(3);
+		svm.setDoNotReplaceMissingValues(false);
+		svm.setEps(0.001);
+		svm.setGamma(0.0);
+		svm.setKernelType(new SelectedTag(LibSVM.KERNELTYPE_RBF, LibSVM.TAGS_KERNELTYPE));
+		svm.setLoss(0.1);
+		svm.setNormalize(false);
+		svm.setNu(0.5);
+		svm.setProbabilityEstimates(false);
+		svm.setSeed(1);
+		svm.setShrinking(true);
 		evaluate(svm);
 	}
 

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/classification/SentimentClassifier.java
replace FastVector by ArrayList since it is deprecated

@@ -67,12 +67,12 @@ public class SentimentClassifier implements ISentimentClassifier {
 			throws ClassificationException {
 		try {
 			Set<String> featureStrings = loadDistinctFeatures(trainingSamples);
-			ArrayList<Attribute> featureList = new FastVector<>();
+			ArrayList<Attribute> featureList = new ArrayList<>();
 			for (String feature : featureStrings) {
 				featureList.add(new Attribute(feature));
 			}
 
-			List<String> sentiments = new FastVector<>();
+			List<String> sentiments = new ArrayList<>();
 			sentiments.add("negative");
 			sentiments.add("positive");
 			Attribute sentimentAttribute = new Attribute("___sentiment___", sentiments);

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/classification/SentimentClassifier.java
clean up the SentimentClassifier

@@ -36,7 +36,7 @@ public class SentimentClassifier implements ISentimentClassifier {
 	public SentimentClassifier(List<TrainingSample> trainingSamples, Classifier algorithm)
 			throws ClassificationException {
 		classifier = new LibSVM();
-		featureList = loadFeatureList(trainingSamples);
+		featureList = createFeatureList(trainingSamples);
 
 		// debug output
 		StringBuilder featureString = new StringBuilder();
@@ -49,7 +49,7 @@ public class SentimentClassifier implements ISentimentClassifier {
 		logger.debug("The following " + featureList.size() + " features are used for classification: [" + featureString + "]");
 
 		featureIndexMap = initFeatureIndexMap(featureList);
-		trainingInstances = loadInstances("train", trainingSamples, featureList);
+		trainingInstances = createInstances("train", trainingSamples, featureList);
 
 		train();
 	}
@@ -63,7 +63,7 @@ public class SentimentClassifier implements ISentimentClassifier {
 		return featureIndexMap;
 	}
 
-	private ArrayList<Attribute> loadFeatureList(Iterable<TrainingSample>trainingSamples)
+	private ArrayList<Attribute> createFeatureList(Iterable<TrainingSample>trainingSamples)
 			throws ClassificationException {
 		try {
 			Set<String> featureStrings = loadDistinctFeatures(trainingSamples);
@@ -90,7 +90,6 @@ public class SentimentClassifier implements ISentimentClassifier {
 		for (TrainingSample trainingSample : trainingSamples) {
 			FeatureVector featureVector = trainingSample.getFeatureVector();
 			for (Feature feature : featureVector.getFeatures()) {
-//				logger.debug("Add feature for word '" + feature.getWord() + "'");
 				features.add(feature.getWord());
 			}
 		}
@@ -105,69 +104,60 @@ public class SentimentClassifier implements ISentimentClassifier {
 		}
 	}
 
-	private Instances loadInstances(String name,
-	                                List<TrainingSample> trainingSamples,
-	                                ArrayList<Attribute> featureList) {
+	/**
+	 * Factory method to create an {@code Instances} object from the given training samples.
+	 */
+	private Instances createInstances(String name,
+	                                  List<TrainingSample> trainingSamples,
+	                                  ArrayList<Attribute> featureList) {
 		Instances instances = new Instances(name, featureList, trainingSamples.size());
[…]

### 2015-01-21 src/main/java/com/aic/Constants.java
set weka version to 3.6.12; add debug output

@@ -2,6 +2,6 @@ package com.aic;
 
 public class Constants {
 
-	public static final String CLASSIFIER_TRAINING_FILE_PATH = "sts_gold_v03.csv";
-	//public static final String CLASSIFIER_TRAINING_FILE_PATH = "training.2000.processed.noemoticon.csv";
+//	public static final String CLASSIFIER_TRAINING_FILE_PATH = "sts_gold_v03.csv";
+	public static final String CLASSIFIER_TRAINING_FILE_PATH = "training.2000.processed.noemoticon.csv";
 }

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/classification/SentimentClassifier.java

@@ -49,7 +49,9 @@ public class SentimentClassifier implements ISentimentClassifier {
 		logger.debug("The following " + featureList.size() + " features are used for classification: [" + featureString + "]");
 
 		featureIndexMap = initFeatureIndexMap(featureList);
+
 		trainingInstances = createInstances("train", trainingSamples, featureList);
+		logger.debug("finished loading of training instances");
 
 		train();
 	}
@@ -134,7 +136,7 @@ public class SentimentClassifier implements ISentimentClassifier {
 	 * Factory method to create an {@code Instance} based on the given feature vector and sentiment value.
 	 */
 	private Instance createInstance(Instances instances, FeatureVector featureVector, Sentiment sentiment) {
-		SparseInstance instance = new SparseInstance(featureList.size());
+		DenseInstance instance = new DenseInstance(featureList.size());
 		instance.setDataset(instances);
 
 		for (Feature feature : featureVector.getFeatures()) {
@@ -144,11 +146,28 @@ public class SentimentClassifier implements ISentimentClassifier {
 		}
 
 		if (sentiment != null) {
-			instance.setValue(featureList.size() - 1, intFromSentiment(sentiment));
+			instance.setClassValue(stringFromSentiment(sentiment));
 		}
 
 		double[] defaultValues = new double[featureList.size()];
 		instance.replaceMissingValues(defaultValues);
+
+		// debug output
+		StringBuilder builder = new StringBuilder();
+		int index = 0;
+		for (double value : instance.toDoubleArray()) {
+			if (value != 0 || index == featureList.size() - 1) {
+				builder.append(featureList.get(index).name());
+				builder.append(',');
+				builder.append(' ');
+			}
+			index++;
+		}
+		if (builder.length() > 0) {
+			builder.delete(builder.length() - 2, builder.length());
+		}
+		logger.debug("created instance: [" + builder + "] for \"" + stringFromSentiment(sentiment)
+				+  "\" message \"" + featureVector.getRawMessage() + "\"");
 
 		return instance;
 	}
@@ -201,10 +220,17 @@ public class SentimentClassifier implements ISentimentClassifier {
 
 	public Evaluation evaluate(List<TrainingSample> testSamples)
 			throws ClassificationException {
+		logger.debug("begin evaluation");
 		Instances testInstances = createInstances("test", testSamples, featureList);
+		logger.debug("finished loading of test instances");
 		try {
[…]

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/feature/FeatureVector.java

@@ -8,12 +8,22 @@ import java.util.List;
 public class FeatureVector {
 
     private List<Feature> features;
+    private String rawMessage;
 
     public void setFeatures(List<Feature> features) {
         this.features = features;
     }
+
     public List<Feature> getFeatures() {
         return features;
+    }
+
+    public String getRawMessage() {
+        return rawMessage;
+    }
+
+    public void setRawMessage(String rawMessage) {
+        this.rawMessage = rawMessage;
     }
 
     @Override

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/preprocessing/SentimentTwitterPreprocessor.java

@@ -56,6 +56,7 @@ public class SentimentTwitterPreprocessor implements ISentimentPreprocessor {
         }
         FeatureVector featureVector = new FeatureVector();
         featureVector.setFeatures(features);
+        featureVector.setRawMessage(message);
 
         return featureVector;
     }

### 2015-01-21 src/test/java/com/aic/sentiment_analysis/classification/EvaluationTest.java

@@ -28,7 +28,8 @@ public class EvaluationTest {
 	public static void loadTrainingData() throws URISyntaxException, PreprocessingException, FileNotFoundException {
 		CSVTrainingSampleLoader sampleLoader = new CSVTrainingSampleLoader();
 		CSVTrainingSTSLoader trainLoader = new CSVTrainingSTSLoader();
-		trainingSamples = trainLoader.load(
+//		trainingSamples = trainLoader.load(
+		trainingSamples = sampleLoader.load(
 				EvaluationTest.class.getClassLoader().getResource(Constants.CLASSIFIER_TRAINING_FILE_PATH).toURI());
 		testSamples = sampleLoader.load(
 				EvaluationTest.class.getClassLoader().getResource(PATH_TO_TEST_DATA).toURI());

### 2015-01-21 src/main/java/com/aic/Constants.java
fix bug in SentimentClassifier

@@ -2,6 +2,6 @@ package com.aic;
 
 public class Constants {
 
-//	public static final String CLASSIFIER_TRAINING_FILE_PATH = "sts_gold_v03.csv";
-	public static final String CLASSIFIER_TRAINING_FILE_PATH = "training.2000.processed.noemoticon.csv";
+	public static final String CLASSIFIER_TRAINING_FILE_PATH = "sts_gold_v03.csv";
+//	public static final String CLASSIFIER_TRAINING_FILE_PATH = "training.2000.processed.noemoticon.csv";
 }

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/classification/SentimentClassifier.java

@@ -35,7 +35,7 @@ public class SentimentClassifier implements ISentimentClassifier {
 	 */
 	public SentimentClassifier(List<TrainingSample> trainingSamples, Classifier algorithm)
 			throws ClassificationException {
-		classifier = new LibSVM();
+		classifier = algorithm;
 		featureList = createFeatureList(trainingSamples);
 
 		// debug output

### 2015-01-21 src/test/java/com/aic/sentiment_analysis/classification/EvaluationTest.java

@@ -28,8 +28,8 @@ public class EvaluationTest {
 	public static void loadTrainingData() throws URISyntaxException, PreprocessingException, FileNotFoundException {
 		CSVTrainingSampleLoader sampleLoader = new CSVTrainingSampleLoader();
 		CSVTrainingSTSLoader trainLoader = new CSVTrainingSTSLoader();
-//		trainingSamples = trainLoader.load(
-		trainingSamples = sampleLoader.load(
+		trainingSamples = trainLoader.load(
+//		trainingSamples = sampleLoader.load(
 				EvaluationTest.class.getClassLoader().getResource(Constants.CLASSIFIER_TRAINING_FILE_PATH).toURI());
 		testSamples = sampleLoader.load(
 				EvaluationTest.class.getClassLoader().getResource(PATH_TO_TEST_DATA).toURI());
@@ -56,30 +56,9 @@ public class EvaluationTest {
 	}
 
 	@Test
-	public void evaluateLibSVM_EPSILON_SVR() throws ClassificationException {
-		LibSVM svm = new LibSVM();
-		svm.setSVMType(new SelectedTag(LibSVM.SVMTYPE_EPSILON_SVR, LibSVM.TAGS_SVMTYPE));
-		evaluate(svm);
-	}
-
-	@Test
 	public void evaluateLibSVM_NU_SVC() throws ClassificationException {
 		LibSVM svm = new LibSVM();
 		svm.setSVMType(new SelectedTag(LibSVM.SVMTYPE_NU_SVC, LibSVM.TAGS_SVMTYPE));
-		evaluate(svm);
-	}
-
-	@Test
-	public void evaluateLibSVM_NU_SVR() throws ClassificationException {
-		LibSVM svm = new LibSVM();
-		svm.setSVMType(new SelectedTag(LibSVM.SVMTYPE_NU_SVR, LibSVM.TAGS_SVMTYPE));
-		evaluate(svm);
-	}
-
-	@Test
-	public void evaluateLibSVM_ONE_CLASS() throws ClassificationException {
-		LibSVM svm = new LibSVM();
-		svm.setSVMType(new SelectedTag(LibSVM.SVMTYPE_ONE_CLASS_SVM, LibSVM.TAGS_SVMTYPE));
 		evaluate(svm);
 	}
 

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/classification/SentimentClassifier.java
fix wrong gradle dependency

@@ -49,9 +49,7 @@ public class SentimentClassifier implements ISentimentClassifier {
 		logger.debug("The following " + featureList.size() + " features are used for classification: [" + featureString + "]");
 
 		featureIndexMap = initFeatureIndexMap(featureList);
-
 		trainingInstances = createInstances("train", trainingSamples, featureList);
-		logger.debug("finished loading of training instances");
 
 		train();
 	}
@@ -146,28 +144,11 @@ public class SentimentClassifier implements ISentimentClassifier {
 		}
 
 		if (sentiment != null) {
-			instance.setClassValue(stringFromSentiment(sentiment));
+			instance.setClassValue(intFromSentiment(sentiment));
 		}
 
 		double[] defaultValues = new double[featureList.size()];
 		instance.replaceMissingValues(defaultValues);
-
-		// debug output
-		StringBuilder builder = new StringBuilder();
-		int index = 0;
-		for (double value : instance.toDoubleArray()) {
-			if (value != 0 || index == featureList.size() - 1) {
-				builder.append(featureList.get(index).name());
-				builder.append(',');
-				builder.append(' ');
-			}
-			index++;
-		}
-		if (builder.length() > 0) {
-			builder.delete(builder.length() - 2, builder.length());
-		}
-		logger.debug("created instance: [" + builder + "] for \"" + stringFromSentiment(sentiment)
-				+  "\" message \"" + featureVector.getRawMessage() + "\"");
 
 		return instance;
 	}
@@ -185,14 +166,6 @@ public class SentimentClassifier implements ISentimentClassifier {
 			return 0;
 		} else {
 			return 1;
-		}
-	}
-
-	private String stringFromSentiment(Sentiment sentiment) {
-		if (sentiment == Sentiment.NEGATIVE) {
-			return "negative";
-		} else {
-			return "positive";
 		}
 	}
 
@@ -220,17 +193,10 @@ public class SentimentClassifier implements ISentimentClassifier {
 
 	public Evaluation evaluate(List<TrainingSample> testSamples)
 			throws ClassificationException {
-		logger.debug("begin evaluation");
 		Instances testInstances = createInstances("test", testSamples, featureList);
-		logger.debug("finished loading of test instances");
 		try {
 			Evaluation evaluate = new Evaluation(trainingInstances);
-			double[] predictions = evaluate.evaluateModel(classifier, testInstances);
-			int i = 0;
-			for (double prediction : predictions) {
[…]

### 2015-01-21 src/main/java/com/aic/rest/controller/CompanyController.java
make classification algorithm configurable

@@ -15,7 +15,6 @@ import org.springframework.web.bind.annotation.*;
 
 import java.util.Date;
 import java.util.Hashtable;
-import java.util.List;
 
 /**
  * Handles the REST requests that are sent to the server.
@@ -97,7 +96,7 @@ public class CompanyController {
 
         // Wrapping aggregateSentiment for Jackson
         AggregateSentiment aggregateSentiment = new AggregateSentiment(
-            sentimentAnalyzer.aggregateSentiment(name, start, end, ClassifierConfiguration.SVM)
+            sentimentAnalyzer.aggregateSentiment(name, start, end, ClassifierConfiguration.SVM_C_SVC)
         );
 
         return aggregateSentiment;

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/ClassifierConfiguration.java

@@ -5,6 +5,10 @@ package com.aic.sentiment_analysis;
  * {@link com.aic.sentiment_analysis.SentimentAnalyzer}.
  */
 public enum ClassifierConfiguration {
-	SVM,
-	NAIVE_BAYES
+	SVM_C_SVC,
+	SVM_NU_SVC,
+	SMO,
+	NAIVE_BAYES,
+	BAYES_NET,
+	KNN
 }

### 2015-01-21 src/main/java/com/aic/sentiment_analysis/SentimentAnalyzer.java

@@ -32,11 +32,23 @@ public class SentimentAnalyzer {
     @Autowired
 	private ISentimentPreprocessor preprocessor;
     @Autowired
-    @Qualifier("svm")
-	private ISentimentClassifier svm;
+    @Qualifier("svm_C_SVC")
+	private ISentimentClassifier svm_C_SVC;
+    @Autowired
+    @Qualifier("svm_NU_SVC")
+	private ISentimentClassifier svm_NU_SVC;
+    @Autowired
+    @Qualifier("smo")
+	private ISentimentClassifier smo;
     @Autowired
     @Qualifier("naiveBayes")
 	private ISentimentClassifier naiveBayes;
+    @Autowired
+    @Qualifier("bayesNet")
+	private ISentimentClassifier bayesNet;
+    @Autowired
+    @Qualifier("kNN")
+	private ISentimentClassifier kNN;
 
     /**
      * Calculates a sentiment value based on an aggregation of tweets and
@@ -88,10 +100,18 @@ public class SentimentAnalyzer {
 
 	private ISentimentClassifier classifierForConfiguration(ClassifierConfiguration config) {
 		switch (config) {
+            case SVM_NU_SVC:
+                return svm_NU_SVC;
+            case SMO:
+                return smo;
 			case NAIVE_BAYES:
 				return naiveBayes;
+            case BAYES_NET:
+                return bayesNet;
+            case KNN:
+                return kNN;
 			default:
-				return svm;
+				return svm_C_SVC;
 		}
 	}
 }

### 2015-01-21 src/main/java/com/aic/rest/controller/CompanyController.java
Enable classifier selection in frontend

@@ -93,11 +93,14 @@ public class CompanyController {
                            @RequestParam(value = "startDate")
                            @DateTimeFormat(pattern = "yyyy-MM-dd") Date start,
                            @RequestParam(value = "endDate")
-                           @DateTimeFormat(pattern = "yyyy-MM-dd") Date end) throws RestException, SentimentAnalysisException {
+                           @DateTimeFormat(pattern = "yyyy-MM-dd") Date end,
+                           @RequestParam(value = "classifier")
+                           ClassifierConfiguration classifier) throws RestException, SentimentAnalysisException {
 
+        System.out.println(classifier);
         // Wrapping aggregateSentiment for Jackson
         AggregateSentiment aggregateSentiment = new AggregateSentiment(
-            sentimentAnalyzer.aggregateSentiment(name, start, end, ClassifierConfiguration.SVM)
+            sentimentAnalyzer.aggregateSentiment(name, start, end, classifier)
         );
 
         return aggregateSentiment;

### 2015-01-21 src/main/resources/static/js/app.js

@@ -5,6 +5,7 @@ var App = angular.module('AngularSpringApp', ['AngularSpringApp.filters',
     'AngularSpringApp.services', 'AngularSpringApp.directives']);
 // Declare app level module which depends on filters, and services
 var sentimentCompany = null;
+var classifiers = null;
 App.config(['$routeProvider', function ($routeProvider) {
     $routeProvider.when('/register', {
         templateUrl: 'templates/register.html',

### 2015-01-21 src/main/resources/static/js/controller/SentimentController.js

@@ -5,6 +5,8 @@
  */
 var SentimentController = function($scope, $http, $location) {
 
+    $scope.range = { start: "2015-01-01", end: "2015-01-25" };
+
     /* Helper function for current active menu in view */
     $scope.isActive = function (viewLocation) {
         var active = (viewLocation === $location.path());
@@ -19,13 +21,14 @@ var SentimentController = function($scope, $http, $location) {
         return false;
     }
 
-    $scope.getCompanySentiment = function(range) {
+    $scope.getCompanySentiment = function(range, classif) {
+        console.log(classif);
         $http.get("sentiment", {
             params: {
                 name: sentimentCompany.name,
-                //password: sentimentCompany.password,
                 startDate: range.start,
-                endDate: range.end
+                endDate: range.end,
+                classifier: classif
             }
         }).success(function(data) {
             $scope.sentiment = data;
@@ -49,8 +52,13 @@ var SentimentController = function($scope, $http, $location) {
         });
 
         $http.get("classifier").success(function(data) {
-            $scope.classifier = data;
-            console.log("classifier loaded");
+            var _cl = [];
+            angular.forEach(data, function(value, key) {
+                _cl.push(value);
+            });
+            classifiers = _cl;
         });
     };
+
+    $scope.classifiers = classifiers;
 };

### 2015-01-21 src/main/resources/static/js/controller/SentimentController.js
Remove console.log output

@@ -22,7 +22,6 @@ var SentimentController = function($scope, $http, $location) {
     }
 
     $scope.getCompanySentiment = function(range, classif) {
-        console.log(classif);
         $http.get("sentiment", {
             params: {
                 name: sentimentCompany.name,

### 2015-01-21 src/main/java/com/aic/rest/controller/CompanyController.java
Remove console.log output

@@ -99,7 +99,7 @@ public class CompanyController {
         System.out.println(classifier);
         // Wrapping aggregateSentiment for Jackson
         AggregateSentiment aggregateSentiment = new AggregateSentiment(
-            sentimentAnalyzer.aggregateSentiment(name, start, end, ClassifierConfiguration.SVM)
+            sentimentAnalyzer.aggregateSentiment(name, start, end, classifier)
         );
 
         return aggregateSentiment;

### 2015-01-21 src/main/resources/static/js/controller/SentimentController.js
Bugfix count not fetch tweets

@@ -31,6 +31,7 @@ var SentimentController = function($scope, $http, $location) {
             }
         }).success(function(data) {
             $scope.sentiment = data;
+            $scope.showErrorAlert = false;
             $scope.showSentiment = true;
         }).error(function(data, status, headers, config){
             $scope.errorTextAlert = "Could not fetch tweets: " + data.message;

### 2015-01-21 paper/chapters/1_introduction.tex
Add Classification corpus

@@
 Furthermore Twitter is able to reach a vast number of potential customers especially for consumer businesses.
-As a result the named services gain more and more acceptance as opinion platforms and powerful tools for both, opinion leader as well as pollister.
-This trend influenced various marketing and sales strategies and created a new market for companies specialiced on sentiment analysis of tweets, like tweetfeel\footnote{\url{www.tweetfeel.com}}, Social Mention\footnote{\url{www.socialmention.com}} and Twitratr\footnote{\url{www.twitratr.com}}.
+As a result the named services gain more and more acceptance as opinion platforms and powerful tools for both, opinion leader as well as pollster.
+This trend influenced various marketing and sales strategies and created a new market for companies specialized on sentiment analysis of tweets, like tweetfeel\footnote{\url{www.tweetfeel.com}}, Social Mention\footnote{\url{www.socialmention.com}} and Twitratr\footnote{\url{www.twitratr.com}}.
 
@@
 English as language allows to express the same intent in different ways.
-The main challenge therefore consists in abstracting the intention of the writer from the grammatic and language specific rules.
+The main challenge therefore consists in abstracting the intention of the writer from the grammatical and language specific rules.
 
 % steps
-In general sentiment analysis can be splitted into 2 steps: a preprocessing and a constitutive sentiment analysis phase.
+In general sentiment analysis can be splitted into two steps: a preprocessing and a constitutive sentiment analysis phase.
 In Twitter sentiment analysis there is another step right bevor preprocessing: fetching the data from the application programming interface (API).
@@
 % a lot research on how sentiment is sentiment is expressed in other media types social quite new
-While sentiment analysis of conventinal ressources like news papers or articles is quite well investigated the special research area of sentiment analysis in terms of social network posts is relatively unexplored.
-Excpecially the possibility of priorizing keywords\footnote{known as hashtags} and the common usage of emoticons lead to advanced possibilities to categorize feelings of posts.
+While sentiment analysis of conventional resources like news papers or articles is quite well investigated the special research area of sentiment analysis in terms of social network posts is relatively unexplored.
+Especially the possibility of priorizing keywords\footnote{known as hashtags} and the common usage of emoticons lead to advanced possibilities to categorize feelings of posts.
 
 \section{Related Work}
-Sentiment analysis a growing and well explored part of Natural Langugage Processing (NLP).
-There are several papers from \citeauthor{Pang2008} regarding sentiment analysis in general and related topics like the effects of various machine learning approaches\autocite{Pang2002}\autocite{Pang2008}.
+Sentiment analysis a growing and well explored part of Natural Language Processing (NLP).
+There are several papers from \citeauthor{Pang2008} regarding sentiment analysis in general and related topics like the effects of various machine learning approaches \autocite{Pang2002}\autocite{Pang2008}.
 Especially the last topic is a well studied field \autocite{Manning2000}.
 Some related research areas are document level classification, sentence-level classification and machine learning.
-Due the limited number of characters within a single twitter post, this topic is quite similar to sentance-level sentiment analysis.
+Due the limited number of characters within a single twitter post, this topic is quite similar to sentence-level sentiment analysis.
 There are several recent papers regarding sentiment analysis in the context of twitter posts.
-\citeauthor{Agarwal2011} published within \citetitle{Agarwal2011} general information and techniques which cover this area\autocite{Agarwal2011}.
+\citeauthor{Agarwal2011} published within \citetitle{Agarwal2011} general information and techniques which cover this area \autocite{Agarwal2011}.
 In \citetitle{Kouloumpis2011} the utility of linguistic features for detecting the sentiment of tweets are investigated.
@@
 Galaxy S) from Twitter Messages, they add a semantic concept (e.g.
-Samsung product) as an additional feature, and measure the correlation of the representative concept with negative/positive sentiment\autocite{Saif2012}.
+Samsung product) as an additional feature, and measure the correlation of the representative concept with negative/positive sentiment \autocite{Saif2012}.
 In \citetitle{Go2009} a algorithm is presented, which accurately classifies tweets as positive or negative, in respect to a query term\autocite{Go2009}.

### 2015-01-21 paper/chapters/4_classification.tex
Add Classification corpus

\section{Classification}
Insert general classification information here.

\begin{enumerate}
\item Supervised vs. unsupervised
\item Training Set
\end{enumerate}

\subsection{Machine Learning Algorithms}
According to the paper by Qiang et al.\autocite{Ye20096527} the most important approaches in 
text mining and sentiment classification are Naive Bayes, SVM and 
N-gram.

\subsubsection{Naive Bayes model for sentiment classification}

\subsubsection{Support vector machines for sentiment classification}

\subsubsection{N-gram based character language model for sentiment classification}

### 2015-01-21 paper/chapters/4_classification.tex
paper

@@
 \section{Classification}
-Insert general classification information here.
+Based on the preprocessed data a machine learning algorithm can be applied which aims to classify the polarity of the given input data. [...]
 
-\begin{enumerate}
-\item Supervised vs. unsupervised
-\item Training Set
-\end{enumerate}
+%Ideen:
+%\begin{enumerate}
+%\item Supervised vs. unsupervised
+%\item Training Set
+%\item FeatureVector
+%\item N-Grams
+%\end{enumerate}
+%
 
@@
 According to the paper by Qiang et al.\autocite{Ye20096527} the most important approaches in 
-text mining and sentiment classification are Naive Bayes, SVM and 
-N-gram.
+text mining and sentiment classification are Naive Bayes, Support Vector Machines and 
+N-gram. Maximum Entropy Classification is also often mentioned by various papers regarding 
+classification in sentiment analysis.
 
@@
 
-\subsubsection{Support vector machines for sentiment classification}
+\subsubsection{Support Vector Machines for sentiment classification}
 
 \subsubsection{N-gram based character language model for sentiment classification}
+
+\subsubsection{Maximum Entropy classification}

### 2015-01-22 paper/chapters/4_methods.tex
paper: some general information about classification; begin description of classifiers

\section{Methods}

Sentiment analysis of twitter data, or more general, the idea of extracting sentiment and opinions from pieces of text is based on the more general principle of \emph{classification} \cite{Pang2002}. The broad aim of classification is to assign given textual units to a set of classes or categories or the apply some kind of regression or ranking. Sentiment analysis is a specialization of this approach which aims at assigning sentiment values to documents. One application might involve to classify an opinionated text by assigning one of two opposing sentiment polarities, i.e. classifying it as either \emph{positive} or \emph{negative}. This classification task is also referred to as \emph{binary classification} or \emph{sentiment polarity classification} \cite{Pang2002}. But in general, the input to the sentiment classification process is not strictly opinionated which makes this task challenging. Therefore this kind of binary classification might not always be applicable. Different approaches that allow for a more fine grained classification might be appropriate, for example, based on a multi-point scale that allows for more than just two sentiment classes.

The characteristics of twitter messages introduce further challenges. Due to the structure of these messages, sentiment analysis of tweets is different from analysing conventional texts, such as review documents, in various ways. The length of at most 140 characters and the rather informal spelling style pose problems that have to be considered carefully when analysing the data. When preprocessing the texts these aspects already need to be handled so that the actual classification process is supplied with information that is considered useful for the analysis phase. After this step it is necessary to collect the relevant information as so called \emph{features} and organize them into a \emph{feature vector}.

\subsection{Features}

TODO

\subsection{Classifiers}

TODO

\subsubsection*{Na\"{\i}ve Bayes}

TODO

\begin{equation*}
P(c \vert d) = \frac{P(c)P(d \vert c)}{P(d)}
\end{equation*}

\begin{equation*}
P_{\mathrm{NB}}(c \vert d) := \frac{P(c)(\prod^{m}_{i=1}P(f_i \vert c)^{n_i(d)})}{P(d)}
\end{equation*}

\subsubsection*{Maimum Entropy}

TODO

\begin{equation*}
P_{\mathrm{ME}}(c \vert d) := \frac{1}{Z(d)}\mathrm{exp}\left( \sum_{i} \lambda_{i,c} F_{i,c}(d,c) \right)
\end{equation*}

\subsubsection*{Support Vector Machines}

TODO

\subsubsection*{Further techniques}

TODO

### 2015-01-22 paper/chapters/4_classification.tex
paper: merge 4_methods.tex and 4_classification.tex

@@
 \section{Classification}
-Based on the preprocessed data a machine learning algorithm can be applied which aims to classify the polarity of the given input data. [...]
 
@@
 
+Sentiment analysis of twitter data, or more general, the idea of extracting sentiment and opinions from pieces of text is based on the more general principle of \emph{classification} \cite{Pang2002}.
+The broad aim of classification is to assign given textual units to a set of classes or categories or the apply some kind of regression or ranking.
+Sentiment analysis is a specialization of this approach which aims at assigning sentiment values to documents.
+One application might involve to classify an opinionated text by assigning one of two opposing sentiment polarities, i.e.
+classifying it as either \emph{positive} or \emph{negative}.
+This classification task is also referred to as \emph{binary classification} or \emph{sentiment polarity classification} \cite{Pang2002}.
+But in general, the input to the sentiment classification process is not strictly opinionated which makes this task challenging.
+Therefore this kind of binary classification might not always be applicable.
+Different approaches that allow for a more fine grained classification might be appropriate, for example, based on a multi-point scale that allows for more than just two sentiment classes.
+
+The characteristics of twitter messages introduce further challenges.
+Due to the structure of these messages, sentiment analysis of tweets is different from analysing conventional texts, such as review documents, in various ways.
+The length of at most 140 characters and the rather informal spelling style pose problems that have to be considered carefully when analysing the data.
+When preprocessing the texts these aspects already need to be handled so that the actual classification process is supplied with information that is considered useful for the analysis phase.
+After this step it is necessary to collect the relevant information as so called \emph{features} and organize them into a \emph{feature vector}.
+
+\subsection{Features}
+
+TODO
+
 \subsection{Machine Learning Algorithms}
+
+Based on the preprocessed data a machine learning algorithm can be applied which aims to classify the polarity of the given input data. [...]
 According to the paper by Qiang et al.\autocite{Ye20096527} the most important approaches in 
@@
 
-\subsubsection{Naive Bayes model for sentiment classification}
+TODO
 
-\subsubsection{Support Vector Machines for sentiment classification}
+\subsubsection*{Na\"{\i}ve Bayes}
 
-\subsubsection{N-gram based character language model for sentiment classification}
+TODO
 
-\subsubsection{Maximum Entropy classification}
+\begin{equation*}
+P(c \vert d) = \frac{P(c)P(d \vert c)}{P(d)}
+\end{equation*}
+
+\begin{equation*}
+P_{\mathrm{NB}}(c \vert d) := \frac{P(c)(\prod^{m}_{i=1}P(f_i \vert c)^{n_i(d)})}{P(d)}
+\end{equation*}
+
+\subsubsection*{Maimum Entropy}
+
+TODO
+
+\begin{equation*}
+P_{\mathrm{ME}}(c \vert d) := \frac{1}{Z(d)}\mathrm{exp}\left( \sum_{i} \lambda_{i,c} F_{i,c}(d,c) \right)
+\end{equation*}
+
+\subsubsection*{Support Vector Machines}
+
+TODO
+
+\subsubsection*{Further techniques}
+
+TODO

### 2015-01-22 paper/chapters/4_classification.tex
paper: add general information about machine learning

@@
 
-\subsection{Machine Learning Algorithms}
+\subsection{Methods}
 
-Based on the preprocessed data a machine learning algorithm can be applied which aims to classify the polarity of the given input data. [...]
-According to the paper by Qiang et al.\autocite{Ye20096527} the most important approaches in 
-text mining and sentiment classification are Naive Bayes, Support Vector Machines and 
-N-gram. Maximum Entropy Classification is also often mentioned by various papers regarding 
-classification in sentiment analysis.
+For the actual classification process extent literature distinguishes two general types of techniques, namely \emph{machine learning} and \emph{semantic orientation} \cite{Ye20096527}.
+The machine learning approach is also referred to as \emph{supervised learning}, since corresponding techniques generally require supervised training phases.
+Accordingly, semantic orientation is also called \emph{unsupervised learning} because such a training phase is not necessary for the process to work.
+The most prominent machine learning methods comprise \emph{support vector machines} and the \emph{Na\"ive Bayes} classifier.
 
-TODO
-
-\subsubsection*{Na\"{\i}ve Bayes}
+\subsubsection*{Na\"ive Bayes}
 

### 2015-01-22 paper/chapters/4_classification.tex
paper: add formular for SVM
Paper: Features

@@
 The characteristics of twitter messages introduce further challenges.
-Due to the structure of these messages, sentiment analysis of tweets is different from analysing conventional texts, such as review documents, in various ways.
-The length of at most 140 characters and the rather informal spelling style pose problems that have to be considered carefully when analysing the data.
+Due to the structure of these messages, sentiment analysis of tweets is different from analyzing conventional texts, such as review documents, in various ways.
+The length of at most 140 characters and the rather informal spelling style pose problems that have to be considered carefully when analyzing the data.
 When preprocessing the texts these aspects already need to be handled so that the actual classification process is supplied with information that is considered useful for the analysis phase.
@@
 \subsection{Features}
-
+As twitter messages are composed of an arbitrary number of words makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets.
+Extracting those words to an object by making use of various word selecting techniques is called a feature vector.
+These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exists.
+	\emph{Term Presence} is a method where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present".
+A similar approach is to count the number of occurred words in a message and use the numeric value as a feature, which is called \emph{Term Frequency} but Pang et al.
+showed \autocite{Pang2008} that Term Presence performed better compared to Term Frequency.
 TODO
@@
 
-TODO
-
 \begin{equation*}
@@
 
-TODO
+\begin{equation*}
+\vec{\omega} := \sum_j \alpha_j c_j \vec{d}_j,\quad \alpha_j \geq 0
+\end{equation*}
 

### 2015-01-22 paper/chapters/4_classification.tex
Paper: Features

@@
 Extracting those words to an object by making use of various word selecting techniques is called a feature vector.
-These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exists.
+These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exist.
 	\emph{Term Presence} is a method where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present".

### 2015-01-22 paper/chapters/4_classification.tex
paper: add description of naive bayes

--- 2015-01-22 paper/chapters/4_classification.tex
@@
 
-TODO
+This technique is based on a simple stochastic model that for a given document $d$ tries to find the most likely class $c^* = \mathrm{arg max}_c P(c \vert d)$ where $c$ stands for one out of a number of possible classes and $P(c \vert d)$ denotes the conditional probability that document $d$ can be assigned to $c$.
+For example, in sentiment analysis $c^*$ would denote the sentiment value that could be assigned to document $d$.
+$c^*$ is computed by applying Bayes' rule,
 
@@
 
+for each possible sentiment value $c$.
+$P(d \vert c)$ has to be estimated and therefore it is presumed that there exists a predefined set of features $\lbrace f_1, \ldots , f_m \rbrace$ which are assumed to be conditionally independent.
+Based on this estimation the actual rule that can be used for classification is derived from Bayes' rule:
+
 \begin{equation*}
@@
 
-\subsubsection*{Maimum Entropy}
+Here, $n_i(d)$ designates the number of occurrences of feature $f_i$ in document $d$.
 
-TODO
+\subsubsection*{Maximum Entropy}
 

### 2015-01-22 paper/chapters/4_classification.tex

--- 2015-01-22 paper/chapters/4_classification.tex
@@
 
+This technique is based on a simple stochastic model that for a given document $d$ tries to find the most likely class $c^* = \mathrm{arg max}_c P(c \vert d)$ where $c$ stands for one out of a number of possible classes and $P(c \vert d)$ denotes the conditional probability that document $d$ can be assigned to $c$.
+For example, in sentiment analysis $c^*$ would denote the sentiment value that could be assigned to document $d$.
+$c^*$ is computed by applying Bayes' rule,
+
 \begin{equation*}
@@
 \end{equation*}
+
+for each possible sentiment value $c$.
+$P(d \vert c)$ has to be estimated and therefore it is presumed that there exists a predefined set of features $\lbrace f_1, \ldots , f_m \rbrace$ which are assumed to be conditionally independent.
+Based on this estimation the actual rule that can be used for classification is derived from Bayes' rule:
 
@@
 
-\subsubsection*{Maimum Entropy}
+Here, $n_i(d)$ designates the number of occurrences of feature $f_i$ in document $d$.
+
+\subsubsection*{Maximum Entropy}
 

### 2015-01-22 paper/chapters/4_classification.tex
Paper: features

--- 2015-01-22 paper/chapters/4_classification.tex
@@
 \subsection{Features}
-As twitter messages are composed of an arbitrary number of words makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets.
-Extracting those words to an object by making use of various word selecting techniques is called a feature vector.
+Since twitter messages are composed of an arbitrary number of words, classification makes it necessary to extract exactly those words which preferably describes the characteristics of such tweets.
+The extraction of those words by the use of various word selecting techniques is called a  feature vector.
 These word selecting techniques are a fundamental process for providing informations to the classification methods, thus an extensive body of different word selecting algorithms exist.
-	\emph{Term Presence} is a method where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present".
-A similar approach is to count the number of occurred words in a message and use the numeric value as a feature, which is called \emph{Term Frequency} but Pang et al.
-showed \autocite{Pang2008} that Term Presence performed better compared to Term Frequency.
-TODO
+An overview is provided by Pang et al.
+\autocite{Pang2008} which can be summarized as follows:\\
+\emph{Term Presence} is a word selecting technique where the feature vector consists of a binary value, $0$ for "term is not present" and $1$ for "term is present".\\
+A similar approach is to count the number of occurred words in a message and make use of the numeric value as a feature, which is called \emph{Term Frequency}.\\
+\emph{Term-based Features Beyond Term Unigrams} describes the encoding of position informations within a textual unit (e.g., at the end of the document)  into the feature vectors.
+This technique is based on the idea that the position of textual units can have influence on the importance of these.\\
+The idea of \emph{Part-of-Speech} (POS) informations is to make use of labeled words within the tweet by diversifying them into categories of words.
+As soon as the words are labeled, they can be filtered (f.e.
+by adjectives and verbs only which can be a strong indicator for sentiment) and the result can be applied to the feature vectors.\\
 

### 2015-01-22 paper/chapters/4_classification.tex
paper: add description of support vector machines

--- 2015-01-22 paper/chapters/4_classification.tex
@@
 
-This technique is based on a simple stochastic model that for a given document $d$ tries to find the most likely class $c^* = \mathrm{arg max}_c P(c \vert d)$ where $c$ stands for one out of a number of possible classes and $P(c \vert d)$ denotes the conditional probability that document $d$ can be assigned to $c$.
+This technique is based on a simple stochastic model that for a given document $d$ tries to find the most likely class $c^* = \mathrm{arg max}_c P(c \vert d)$ where $c$ stands for one out of a number of possible classes and $P(c \vert d)$ denotes the conditional probability that document $d$ can be assigned to $c$ \cite{Pang2002}.
 For example, in sentiment analysis $c^*$ would denote the sentiment value that could be assigned to document $d$.
@@
 \begin{equation*}
-P_{\mathrm{NB}}(c \vert d) := \frac{P(c)(\prod^{m}_{i=1}P(f_i \vert c)^{n_i(d)})}{P(d)}
+P_{\mathrm{NB}}(c \vert d) := \frac{P(c)(\prod^{m}_{i=1}P(f_i \vert c)^{n_i(d)})}{P(d)}.
 \end{equation*}
@@
 
-\subsubsection*{Maximum Entropy}
+\subsubsection*{Support Vector Machines}
+
+In contrast to the above method, support vector machines (SVMs) do not use a probabilistic model.
+Instead the aim of this technique is to find a so called \emph{hyperplane}, which is represented by a vector $\vec{\omega}$.
+Let $\vec{d} := (n_1(d), n_2(d),\ldots , n_m(d))$ be the \emph{document vector} of document $d$ where, like above, $n_i(d)$ represents the number of occurrences of feature $f_i$ in $d$.
+Then, in the case of a binary classification problem, $\vec{\omega}$ separates the document vectors in one class from the vectors in the other class such that this separation (the so called \emph{margin}) is as large as possible.
+To find $\vec{\omega}$, a dual optimization problem has to be solved, to find for each document $d_j$ a value $\alpha_j$ such that the following holds:
 
 \begin{equation*}
-P_{\mathrm{ME}}(c \vert d) := \frac{1}{Z(d)}\mathrm{exp}\left( \sum_{i} \lambda_{i,c} F_{i,c}(d,c) \right)
+\vec{\omega} := \sum_j \alpha_j c_j \vec{d}_j,\quad \alpha_j \geq 0,
 \end{equation*}
 
-\subsubsection*{Support Vector Machines}
-
-\begin{equation*}
-\vec{\omega} := \sum_j \alpha_j c_j \vec{d}_j,\quad \alpha_j \geq 0
-\end{equation*}
+where $c_j \in \lbrace 1, -1\rbrace$ (in sentiment classification $1$ would denote "positive" and correspondingly $-1$ stands for "negative" sentiment).
+The actual classification of document $d$ is done, by determining on which side of $\vec{omega}$ its document vector $\vec{d}$ falls on.
 

### 2015-01-22 paper/chapters/4_classification.tex
paper: remove typo
paper: further techniques

@@
 where $c_j \in \lbrace 1, -1\rbrace$ (in sentiment classification $1$ would denote "positive" and correspondingly $-1$ stands for "negative" sentiment).
-The actual classification of document $d$ is done, by determining on which side of $\vec{omega}$ its document vector $\vec{d}$ falls on.
+The actual classification of document $d$ is done, by determining on which side of $\vec{\omega}$ its document vector $\vec{d}$ falls on.
 
 \subsubsection*{Further techniques}
-
-TODO
+Beside Na\"ive Bayes and Support Vector Machines various other machine learning techniques such as Character based N-gram model, Maximum entropy, Random Forest and J48 exist and are just mentioned here for the sake of completeness, a comprehensive view of other machine learning techniques is beyond the scope of this survey.

### 2015-01-23 slides/presentation-2.tex
Add slides for second presentation

--- 2014-12-05 slides/presentation-1.tex
@@
 \institute{Advanced Internet Computing}
-\date{5th December 2014}
+\date{29th January 2015}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{frame}{Twitter API}
-Twitter offers several APIs for different purposes. All require authorization and a valid Twitter API-account.
+\begin{frame}{Scope of Stage 2}
 
 \begin{itemize}
-	\item REST API
+ \item Wrap sentiment analysis application into a simple Web service
+ \item Provide a GUI for testing and demonstrating the service
+ \item Experiment with different algorithms to improve original implementation
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}{Web service}
+We implemented a RESTful Web service by the use of Spring MVC which allows to register a company 
+and fetch the general feeling (sentiment) of the Twitter community about that company.
 \begin{itemize}
-    	\item limited to 180 GET-Request/Minute
-        \item fetch all tweets at once
-    \end{itemize}
-    \item Streaming API
+ \item \emph{/register:} Register company 
+ \item \emph{/sentiment:} Fetch sentiment of the registered company by params:
   \begin{itemize}
-    	\item no limitation regarding tweets per minute
-        \item continuous tweet-stream
+	\item \emph{name} - the name of the company
+	\item \emph{startDate} - start date range (Format: yyyy-MM-dd)
+	\item \emph{endDate} - end date range (Format: yyyy-MM-dd)
+	\item \emph{classifier} - the classifier (\emph{SVM\_C\_SVC}, \emph{SVM\_NU\_SVC}, \emph{SMO}, \emph{NAIVE\_BAYES}, \emph{BAYES\_NET} or \emph{KNN})
  \end{itemize}
@@
 
-% Commands to include a figure:
-%\begin{figure}
-%\includegraphics[width=\textwidth]{your-figure's-file-name}
-%\caption{\label{fig:your-figure}Caption goes here.}
-%\end{figure}
-
-\begin{frame}{Preprocessing}
-\begin{block}{}
-Preprocess a tweet message and extract important information (feature vector) for classification.
-\end{block}
+\begin{frame}{Web interface}
+A simple Web interface GUI was implemented to interact with the REST Web service
 \begin{itemize}
-	\item[Tokenizer]
-    splits input into related parts (tokens). e.g. Stanford NLP PTBTokenizer, Carnegie Mellon Twokenizer
-	\item[Tagger]
-    adds information to each token (e.g. word-class).  e.g Stanford NLP MaxentTagger
-	\item[Filter token list] 
-    filtering based on tagged-information. 
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}{Classification}
-%\begin{block}{}
-%Classification aims at dividing inputs into at least two classes by the use of a learned model.
-%\end{block}
-\begin{itemize}
-	\item Aims at dividing inputs into at least two classes
-    \item In this course: assign sentiments to textual inputs
-    \item Supervised and unsupervised approaches
-    \item Common supervised algorithms: Support vector machines (SVM), naive bayes, \ldots
-    \begin{itemize}
-        \item Textual input in form of a \emph{feature vector}
-        \item The feature vector contains relevant words such as verbs, adjectives and hashtags
-    \end{itemize}
+ \item Bootstrap\footnote{http://getbootstrap.com} HTML/CSS/JS Framework
+ \item AngularJS\footnote{http://angularjs.org} for REST interaction
 \end{itemize}
@@
 
-\begin{frame}{Classification (Implementation)}
+\begin{frame}{Classification Algorithms}
+TODO
   \begin{itemize}
-	\item Based on WEKA
-    \item SVM as classifier (LibSVM)
-    \item Train model with stanford twitter test corpus\footnote{\tiny{http://help.sentiment140.com/for-students}} (manually reduced to 1000 positive and 1000 negative instances)
-	\item Evaluation with testset (359 instances):\\ \textbf{64.35 \%} classified correctly
+	\item Support Vector Machine C SVC
+	\item Support Vector Machine Nu SVC
+	\item SMO
+	\item Na\"ive Bayes
+	\item Bayes Net
+	\item K-Nearest Neighbour
  \end{itemize}
@@
 
-\begin{frame}{Aggregate Classified Sentiments}
-Calcuate the weighted sentiment for each tweet whereby more recent dates are weighted heavier
+\begin{frame}{Evaluation Results}
+TODO
+\end{frame}
+
+\begin{frame}{Lessions learned/Conclusion}
+TODO
 \begin{itemize}
-	\item The weight of the most recent positive tweet is 1
-    \item The weight of the oldest is 0.8
-    \item The weights in between decrease linear
-    \item $\sum_{i = 0}^{\#tweets-1}1-i*\frac{decreaseFactor}{\#tweets-1}$
-    \item Just positive tweets are weighted
+ \item Classification accuracy is strongly depended on (quality of) the training set
+ \item ...
  \end{itemize}
@@
 
-\begin{frame}{Prototype}
-Some libraries and attributes of our prototype.
-
-\begin{itemize}
-	\item Spring Boot
-    \item REST Backend
-    \item AngularJS Frontend
-    \item PTBTokenizer and Twokenizer
-    \item Maxent Tagger
-    \item Weka
-\end{itemize}
-
-\begin{block}{}
-$\rightarrow$ live demo!
-\end{block}
-
-\begin{block}{}
-Code available at: https://github.com/inkrement/aic
-\end{block}
-
-\end{frame}
-
 \end{document}

### 2015-01-24 paper/chapters/1_introduction.tex
Typos

@@
 % steps
-In general sentiment analysis can be splitted into two steps: a preprocessing and a constitutive sentiment analysis phase.
-In Twitter sentiment analysis there is another step right bevor preprocessing: fetching the data from the application programming interface (API).
+In general, sentiment analysis can be splitted into two steps: a preprocessing and a constitutive sentiment analysis phase.
+In Twitter sentiment analysis there is another step right before preprocessing: fetching the data from the application programming interface (API).
 This task is not trivial, because the official API is limited regarding the datasets fetched within certain intervals.
@@
 Samsung product) as an additional feature, and measure the correlation of the representative concept with negative/positive sentiment \autocite{Saif2012}.
-In \citetitle{Go2009} a algorithm is presented, which accurately classifies tweets as positive or negative, in respect to a query term\autocite{Go2009}.
+In \citetitle{Go2009}, an algorithm is presented, which accurately classifies tweets as positive or negative in respect to a query term\autocite{Go2009}.

### 2015-01-24 paper/chapters/3_preprocessing.tex
Typos

@@
 \subsection{Tagger}
-Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefor
+Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefore
 very useful for Natural Language Processing.
@@
 %TODO: Quelle: Part-of-Speech Tagging for Twitter: Annotation, Features, and Experiments
+spelling errors, bad structure, abbreviations, and slang
+%TODO Quelle: Mirroring the Real World in Social Media: Twitter, Geolocation, and Sentiment Analysis
 There is a variety of freely downloadable POS taggers

### 2015-01-24 paper/chapters/5_conclusions.tex
Conclusion added

\section{Conclusions}
Due to the growing number of users and Tweets, Twitter sentiment analsyis is a growing field. Sentiment analysis itself is a well explored part of NLP, but the analsysis of Twitter posts is not as bridely investigated as for conventional resources like news papers or articles.

However, the analysis of tweets is more like the sentence-level but the paragraph-level analsyis due to their short length, which also leads to other problems as the use of slang, emoticons and other uncommon sentence parts. To prepare the data, the preprocessing phase to remove URLs, unnecessary words, retweets and repeated characters is an important part for the analsysis. For this task, several tokenizers and taggers are available. The relevant information ("features") is then determined and classified with the support vector machine or the Na\"ive Bayes method.

We saw that Twitter sentiment analsis is an important research field but needs some more works to improve the quality and accuracy of both preprocessing and classifying the content of a tweet.

### 2015-01-24 paper/chapters/3_preprocessing.tex
edit tagger section of the paper

--- 2014-11-30 paper/chapters/3_preprocessing.tex
@@
 Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefor
-very useful for Natural Language Processing.
-Tagging Tweets is very challenging, because of the twitter specific slang, emoticons and the lack of conventional orthography.
-%TODO: Quelle: Part-of-Speech Tagging for Twitter: Annotation, Features, and Experiments
-There is a variety of freely downloadable POS taggers
-\footnote{http://www-nlp.stanford.edu/links/statnlp.html} e.g. Stanford POS tagger
-\footnote{http://nlp.stanford.edu/software/tagger.shtml}
- but just a few are specialized on tagging twitter data like the TweetNLP tagger
-\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}. In comparison with the Stanford POS tagger the TweetNLP tagger
- reduces errors by 25\%.
- %TODO Quelle: http://iswc2012.semanticweb.org/sites/default/files/76490497.pdf
+very useful for Natural Language Processing. The performance of POS taggers degrade
+on out-of-domain data and tagging tweets poses additional challenges, e.g. the twitter
+specific slang, emoticons and the lack of conventianal orthography. \autocite{Gimpel2011}
+There is already a wide range of freely downloadable POS taggers \footnote{http://www-nlp.stanford.edu/links/statnlp.html},
+e.g. the Standford POS tagger \footnote{http://nlp.stanford.edu/software/tagger.shtml}.
+Because of the peculiarities of the language used in tweets, just a few of them are
+specialized on tagging twitter data, like the TweetNLP tagger \footnote{http://www.ark.cs.cmu.edu/TweetNLP/}.
+In comparison with the Stanford POS tagger the TweetNLP tagger reduces errors by 25\%. \autocite{Saif2012}

### 2015-01-24 src/main/java/com/aic/sentiment_analysis/fetch/Cache.java
JavaDoc added

@@ -7,19 +7,34 @@ import java.util.Date;
 import java.util.List;
 
 /**
- * @todo implement
+ * This class provides the caching functionality.
  */
-
-public class Cache
-{
-    public static final String PATH = "tmp" +  File.separator + "cache" + File.separator;
+/**
+ * @author Florian Taus
+ *
+ */
+/**
+ * @author Florian Taus
+ */
+/**
+ * @author Florian Taus
+ */
+public class Cache {
+	/** The path of the cache files. */
+	public static final String PATH = "tmp" + File.separator + "cache" + File.separator;
 
 	/**
-	 * loads a list of already cached datasets cuts overlapping parts that are
-	 * not in the given timerange
+	 * Loads a list of already cached datasets and cuts overlapping parts that are not in the given timerange.
+	 *
+	 * @param name
+	 *            The keyword
+	 * @param start
+	 *            The start date of the timerange
+	 * @param end
+	 *            The end date of the timerange
+	 * @return A list of twitter status lists
 	 */
-	public static List<TwitterStatusList> load(String name, Date start, Date end)
-	{
+	public static List<TwitterStatusList> load(String name, Date start, Date end) {
 		List<TwitterStatusList> result = new ArrayList<TwitterStatusList>();
 
 		// find all files matching name_*
@@ -27,15 +42,13 @@ public class Cache
 
 		// parse timestamps and eventually load files
 		System.out.println("Files for " + name + ": " + files.length);
-		for (File f: files)
-		{
+		for (File f: files) {
 			String[] parts = f.getName().split("_");
 			Date f_start = new Date(Long.parseLong(parts[1], 10));
 			Date f_end = new Date(Long.parseLong(parts[2], 10));
 			System.out.println(f.getAbsolutePath() + ": start: " + f_start + ", end: " + f_end);
 			boolean b = overlap(f_start, f_end, start, end);
-			if (b)
-			{
+			if (b) {
 				// load list and trim it to fit timerange
 				result.add(loadFile(f).trim(start, end));
 			}
@@ -49,40 +62,36 @@ public class Cache
 		return result;
 	}
 
-    /**
-     *
-     * @param tweets
-     * @return
-     * @throws IOException
-     */
+	/**
+	 * Stores the list {@code tweets} into a file.
+	 * 
+	 * @param tweets
+	 *            The list of tweets
[…]

### 2015-01-24 src/main/java/com/aic/sentiment_analysis/fetch/Fetch.java

@@ -12,17 +12,15 @@ import java.util.*;
 
 /**
  * The class for fetching tweets.
- * 
- * @author Florian Taus
  */
 @Component
 public class Fetch implements ITweetLoader {
 
+	/** The maximum number of tweets to be fetched at once. */
 	public static final int MAX_TWEETS = 50;
 
 	private static final Log logger = LogFactory.getLog(Fetch.class);
 	private static final SimpleDateFormat dateFormat = new SimpleDateFormat("YYYY-MM-dd");
-
 	private Configuration configuration;
 
 	@Autowired
@@ -30,6 +28,19 @@ public class Fetch implements ITweetLoader {
 		this.configuration = configuration;
 	}
 
+	/**
+	 * Loads the tweets for a given {@code name} and a given period of time, i.e. calling {@link #fetch(String, Date, Date, long, long)} with the apropriate
+	 * parameters.
+	 * 
+	 * @param name
+	 *            The keyword
+	 * @param start
+	 *            The start date
+	 * @param end
+	 *            The end date
+	 * @see #fetch(String, Date, Date, long, long)
+	 * @see com.aic.sentiment_analysis.fetch.ITweetLoader#load(java.lang.String, java.util.Date, java.util.Date)
+	 */
 	public List<TwitterStatus> load(String name, Date start, Date end) {
 		Calendar cal = Calendar.getInstance();
 		cal.setTime(end);
@@ -38,63 +49,38 @@ public class Fetch implements ITweetLoader {
 		cal.set(Calendar.SECOND, 59);
 		end = cal.getTime();
 		logger.debug("\n" + name + " (" + start + "-" + end + ")");
-		
+
 		List<TwitterStatus> result = new ArrayList<TwitterStatus>();
-//		List<TwitterStatusList> cached_tweets = Cache.load(name, start, end);
-//		System.out.println("1: " + start);
-//		Collections.sort(cached_tweets);
-//		System.out.println("2: " + start);
-//		System.out.println("Number of cached tweet lists: " + cached_tweets.size());
 
 		long startId = 0;
 		long endId;
-//		for (TwitterStatusList tsl: cached_tweets)
-//		{
-//			System.out.println("Cached file: start: " + tsl.getStart() + ", end: " + tsl.getEnd());
-//			endId = tsl.getStartId() - 1;
-//			System.out.println("3: " + start);
-//			System.out.println("Start of range: " + start + ", start of file: " + tsl.getStart());
[…]

### 2015-01-24 src/main/java/com/aic/sentiment_analysis/fetch/TwitterStatus.java

@@ -6,18 +6,26 @@ import twitter4j.Status;
 import java.io.Serializable;
 import java.util.Date;
 
-public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
-{
+/**
+ * This class represents a twitter status with the important information needed for a sentiment analsysis.
+ */
+public class TwitterStatus implements Serializable, Comparable<TwitterStatus> {
 	private static final long serialVersionUID = 7526472295654436147L;
 
 	private long id;
-    private int favouriteCount;
+	private int favouriteCount;
 	private int retweetCount;
 	private Place location;
 	private String username;
 	private String text;
 	private Date timestamp;
 
+	/**
+	 * Creates a new twitter status from a Twitter4J status.
+	 * 
+	 * @param twitter4jstatus
+	 *            The Twitter4J status
+	 */
 	public TwitterStatus(Status twitter4jstatus) {
 		id = twitter4jstatus.getId();
 		timestamp = twitter4jstatus.getCreatedAt();
@@ -28,10 +36,8 @@ public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 		text = twitter4jstatus.getText();
 	}
 
-	/**
-	 * only for testpurposes
-	 */
-	public TwitterStatus(Date timestamp, String username, String text) {
+	/* Just for testing */
+	protected TwitterStatus(Date timestamp, String username, String text) {
 		this.timestamp = timestamp;
 		this.favouriteCount = 0;
 		this.retweetCount = 0;
@@ -40,34 +46,33 @@ public class TwitterStatus implements Serializable, Comparable<TwitterStatus>
 		this.id = -1;
 	}
 
-	public long getId()
-	{
+	public long getId() {
 		return id;
 	}
 
-    public int getRetweetCount() {
-        return retweetCount;
-    }
+	public int getRetweetCount() {
+		return retweetCount;
+	}
 
-    public void setRetweetCount(int retweetCount) {
-        this.retweetCount = retweetCount;
-    }
+	public void setRetweetCount(int retweetCount) {
+		this.retweetCount = retweetCount;
+	}
 
-    public int getFavouriteCount() {
-        return favouriteCount;
-    }
+	public int getFavouriteCount() {
+		return favouriteCount;
+	}
 
-    public void setFavouriteCount(int favouriteCount) {
-        this.favouriteCount = favouriteCount;
-    }
+	public void setFavouriteCount(int favouriteCount) {
+		this.favouriteCount = favouriteCount;
+	}
 
[…]

### 2015-01-24 src/main/java/com/aic/sentiment_analysis/fetch/TwitterStatusList.java

@@ -3,88 +3,117 @@ package com.aic.sentiment_analysis.fetch;
 import java.util.ArrayList;
 import java.util.Date;
 
-// TODO javadoc	
-public class TwitterStatusList extends ArrayList<TwitterStatus> implements Comparable<TwitterStatusList>
-{
+/**
+ * Represents a list of twitter statuses.
+ *
+ * @see TwitterStatus
+ */
+/**
+ * @author Florian Taus
+ *
+ */
+/**
+ * @author Florian Taus
+ */
+public class TwitterStatusList extends ArrayList<TwitterStatus> implements Comparable<TwitterStatusList> {
 	private static final long serialVersionUID = -445662097030771988L;
 	private String keyword;
 	private Date start;
 	private Date end;
 
-	private TwitterStatusList()
-		{
-			super();
-		}
-
-	public TwitterStatusList(String keyword)
-		{
-			this();
-			this.keyword = keyword;
-		}
+	private TwitterStatusList() {
+		super();
+	}
 
 	/**
-	 * return starting timestamp
+	 * Creates a new status list for the given keyword
+	 * 
+	 * @param keyword
+	 *            The keyword
 	 */
-	public Date getStart()
-	{
+	public TwitterStatusList(String keyword) {
+		this();
+		this.keyword = keyword;
+	}
+
+	/**
+	 * Returns the start date.
+	 * 
+	 * @return The start date
+	 */
+	public Date getStart() {
 		return start;
 	}
 
-	public long getStartId()
-	{
+	/**
+	 * Returns the start ID.
+	 * 
+	 * @return The start ID
+	 */
+	public long getStartId() {
 		return size() == 0 ? 0 : this.get(0).getId();
 	}
 
-	public long getEndId()
-	{
+	/**
+	 * Returns the end ID.
+	 * 
+	 * @return The end ID
+	 */
+	public long getEndId() {
 		return size() == 0 ? Long.MAX_VALUE : this.get(this.size() - 1).getId();
 	}
 
 	/**
-	 * return ending timestamp
+	 * Returns the end date.
+	 * 
+	 * @return The end date
 	 */
-	public Date getEnd()
-	{
+	public Date getEnd() {
 		return end; // to get last
 	}
 
-	public String getKeyword()
-	{
+	/**
+	 * Returns the keyword.
+	 * 
+	 * @return The keyword
+	 */
+	public String getKeyword() {
 		return keyword;
 	}
 
[…]

### 2015-01-25 paper/chapters/5_conclusions.tex
Conclusion extended

@@
 \section{Conclusions}
-Due to the growing number of users and Tweets, Twitter sentiment analsyis is a growing field.
-Sentiment analysis itself is a well explored part of NLP, but the analsysis of Twitter posts is not as bridely investigated as for conventional resources like news papers or articles.
+Due to the growing number of users and Tweets, Twitter sentiment analysis is a growing field.
+Sentiment analysis itself is a well explored part of NLP, but the analysis of Twitter posts is not as widely investigated as for conventional resources like newspapers or articles.
 
-However, the analysis of tweets is more like the sentence-level but the paragraph-level analsyis due to their short length, which also leads to other problems as the use of slang, emoticons and other uncommon sentence parts.
-To prepare the data, the preprocessing phase to remove URLs, unnecessary words, retweets and repeated characters is an important part for the analsysis.
-For this task, several tokenizers and taggers are available.
-The relevant information ("features") is then determined and classified with the support vector machine or the Na\"ive Bayes method.
+However, the analysis of tweets is more like the sentence-level than the paragraph-level analysis due to their short length, which also leads to other problems as the use of slang, emoticons and other uncommon sentence parts.
+To prepare the data, URLs, unnecessary words, retweets and repeated characters are removed in the preprocessing phase.
+The use of the right tagger, which ought to be a tagger specialized for Tweets, is important due to the big differences, e.g.
+TweetNLP has 25 percent less errors than the Stanford POS tagger.
 
-We saw that Twitter sentiment analsis is an important research field but needs some more works to improve the quality and accuracy of both preprocessing and classifying the content of a tweet.
+The relevant information (``features'') is then determined and classified with the support vector machine or the Na\"ive Bayes method.
+The Na\"ive Bayer method classifies documents based on the Bayes' rule, while support vector machines are trained to create a hyperplane that separates the two classes (``positive'' and ``negative'' in sentiment classification), so that Tweets can be classified as above or below this hyperplane.
+
+We saw that Twitter sentiment analysis is an important research field but needs some more works to improve the quality and accuracy of both preprocessing and classifying the content of a tweet.

### 2015-01-25 paper/chapters/5_conclusions.tex
Conclusion extended

@@
 \section{Conclusions}
-Due to the growing number of users and Tweets, Twitter sentiment analysis is a growing field.
+Due to the emerging number of users and Tweets, Twitter sentiment analysis is a growing field.
 Sentiment analysis itself is a well explored part of NLP, but the analysis of Twitter posts is not as widely investigated as for conventional resources like newspapers or articles.
@@
 To prepare the data, URLs, unnecessary words, retweets and repeated characters are removed in the preprocessing phase.
-The use of the right tagger, which ought to be a tagger specialized for Tweets, is important due to the big differences, e.g.
+The use of the right tagger, which ought to be a tagger specialized for Tweets, is important because of the big differences, e.g.
 TweetNLP has 25 percent less errors than the Stanford POS tagger.
@@
 The relevant information (``features'') is then determined and classified with the support vector machine or the Na\"ive Bayes method.
-The Na\"ive Bayer method classifies documents based on the Bayes' rule, while support vector machines are trained to create a hyperplane that separates the two classes (``positive'' and ``negative'' in sentiment classification), so that Tweets can be classified as above or below this hyperplane.
+The Na\"ive Bayes method classifies documents based on the Bayes' rule while support vector machines are trained to create a hyperplane that separates the two classes (``positive'' and ``negative'' in sentiment classification), so that Tweets can be classified as above or below this hyperplane.
 
-We saw that Twitter sentiment analysis is an important research field but needs some more works to improve the quality and accuracy of both preprocessing and classifying the content of a tweet.
+We saw that Twitter sentiment analysis is an important research field but needs some more work to improve the quality and accuracy of both preprocessing and classifying the content of a tweet.
